### 2011-12-06 paper.tex
added paper latex and pdf

%% bare_conf.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[conference]{IEEEtran}
% Add the compsoc option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUBFIGURE PACKAGES ***
%\usepackage[tight,footnotesize]{subfigure}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.

%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Documentation is contained in the stfloats.sty comments as well as in the
% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
% does not allow \baselineskip to stretch. Authors submitting work to the
% IEEE should note that IEEE rarely uses double column equations and
% that authors should try to avoid such use. Do not be tempted to use the
% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
% not format its papers in such ways.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{PBJ: A Gnutella Inspired File Sharing System }

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Camden Clements}
\IEEEauthorblockA{School of Computing\\
Clemson University\\
Clemson, SC 29632\\
Email: camdenc@gmail.com}
\and
\IEEEauthorblockN{Adam Hodges}
\IEEEauthorblockA{School of Computing\\
Clemson University\\
Clemson, SC 29632\\
Email: hodges8@clemson.edu}
\and
\IEEEauthorblockN{Zach Welch}
\IEEEauthorblockA{School of Computing\\
Clemson University\\
Clemson, SC 29632\\
Email: zwelch@clemson.edu}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

\begin{abstract}
%\boldmath
PBJ is a distributed file sharing system designed on many of the same principles of the gnutella file sharing application.  Rather than route search requests through some central entity like Napster and to a lesser extent BitTorrent, PBJ creates a network of connected users.  Search requests are broadcast between users and files are downloaded directly between them.  This paper details the algorithms behind PBJ, the specifics of its implementation, and a comparison of PBJ to other popular file sharing systems.  Future improvements to PBJ are also discussed.   
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
Peer to peer (P2P) file sharing is probably one of the most well known and ubiquitous examples of a distributed system.  These systems allow users to search for and download files stored on the machines of other users.  Systems such as Napster, BitTorrent, and Gnutella are used by millions of people every day to download files.  While the content on these systems is not always legal (eg. file sharing of media such as music and movies), P2P file sharing networks are..... File sharing is an ideal case study of distributed systems, and highlight many of the design decisions faced when developing such systems. P2P systems can feature a number of different network topographies that range from having a central server storing all the files (Napster) to a distributed system with almost no centralized elements (Gnutella).  In the sections that follow we document and describe PBJ, our P2P file sharing system influenced by Gnutella.

\subsection{Background}
\subsubsection{Napster}
A defining characteristic of a P2P file sharing application is the kind of network topology it employs.  Napster, one of the first file sharing networks, was a highly centralized system.  All  online Napster users connected to a central server.  Each user would have a folder designated for sharing audio files (only mp3s were transferred on Napster).  This central server would handle a user request by searching for related files in the share folders of other users.  The central server would then report a list of relevant files and their locations that the user could choose to download.  Any files the requesting user chose to download would directly connect with the associated machine for actual file transfer.  The ``flaw'' of Napster's system is that the central server is appropriately named; if the server goes down, then the network ceases to exist because no requests can be processed.  This is exactly what happened in 2001 when the inevitable flood of copyright infringement lawsuits were filed against Napster.  File sharing applications developed after Napster’s shut down attempted to avoid this problem by making the system less centralized. 
\subsubsection{BitTorrent}
 Most file sharing today uses the BitTorrent protocol.  BitTorrent differs from other file sharing systems in that where as Napster and gnutella transfer entire files between nodes, BitTorrent downloads parts of the file from multiple sources.  BitTorrent works by having a user obtain a torrent file (usually by downloading it from a website).  The local BitTorrent client interprets the contents of the torrent file and connects with a tracker, a server with information about how to find the file. The tracker finds seeders, other BitTorrent clients with a local copy of the file to be transferred. The file also identifies the swarm, a set of clients with a portion of the file, usually in the process of downloading it themselves.  The searching client downloads from these sources simultaneously to build the desired file.  BitTorrent is especially useful for downloading popular files, since there will be a large pool of seeders and a large swarm.  While BitTorrent is clearly more distributed than Napster, since their are multiple central servers instead of a single large server for the entire application.  However, if the tracker(s) in a torrent file are taken down, there is no way that torrent file can be used to obtain the actual file.     
 \subsubsection{Gnutella}
 Gnutella (a portmanteau of GNU, the free software project, and Nutella, the chocolate and hazelnut spread) is a decentralized network of interconnected users running a gnutella client called a node.  Search requests are broadcast to all of the searching node’s neighbor clients (which gnutella terms “peers”), which in turn broadcast the request to all of their peers as well.  This goes on until the file is found or the request goes a specified number of peer hops without finding a file (much like the time to live field in an IP packet). This does allow for the possibility that a search request may fail to return a file in the network. Later versions of gnutella’s network introduced the concept of ultra nodes and ultra peers. Each ultra node is connected to a network of regular nodes and a large number of other ultra nodes, each with its own network of nodes, making gnutella a network of networks.  The reasons for this change is that it many more nodes can be reached from any one node in a few hops, making searching more efficient and the system more scalable.  Nodes keep track of nodes and ultra nodes they have previously connected with and attempt to reconnect to the network through these nodes.  When connecting for the first time, these nodes must attempt to a set of nodes guaranteed to be in the gnutella network.  This means that despite the highly decentralized nature of gnutella, a few centralized elements remain.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals/conferences use top floats
% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
% command of the stfloats package.

\section{Methodology}

PBJ takes the key qualities of gnutella and uses them as a starting point, rather than implement a version of the gnutella client.  LIke gnutella, PBJ contains a network of ultra nodes.  In PBJ, each ultra node has a set of nodes.  Note that ultra nodes are also nodes in PBJ.  If there are k nodes per ultra node, the first node to be added to the network will become an ultra node, the next k nodes will be added to the ultra node.  The k+1th node will then become a new ultra node.  Ultra nodes in PBJ are given a unique ID.  This unique ID is a vital element to building the network. The basic algorithm for creation of the network builds an outward spiral of ultra peers.  While this alone would be wildly inefficient in terms of searching and stability, new ultra nodes also connect to ultra nodes deeper within the spiral.  This allows search requests to quickly move between otherwise distant ultra nodes. More specifically, the first node created will be given an ID of 0, the second an ID of 1, etc.  When a node is created with ID Y, it will attempt to connect to all nodes X, 0 < X < Y, where Y - X = 2Z, Z being an even integer.  So for example, node 16 would connect with node 15 (16 - 15 = 1 = 20), node 12 (16 - 12 = 4 = 22), and node 0 (16 - 0 = 16 = 24). To make talking about the network easier, we delineate between kinds of hops between nodes.  For example, a hop from 5 to 6 is a 1-hop, where a hop from 5 to 9 is a 4-hop etc.

The PBJ network structure presents several clear benefits.  The first clear gain is that the PBJ network is that there is a high level of redundancy in the connections.  This means that the nodes are connected in such a way that it is easy for search requests to reach most if not all of the nodes on the network in a few hops.  Currently, building the network is done through a predefined gateway at a predefined IP address and port.  The gateway keeps track of all the ultrapeers in the system.  When a new node tries to join the system, the gateway makes several decisions based on the current status of the PBJ network.  First, the gateway decides if the new node will become an ultra node.  If so, it will give the new ultra node a list of other ultra nodes to connect to.  If the new node is not an ultra peer, the gateway will provide information on the appropriate ultra peer sub network to join. These decisions by the gateway essentially dictate how the network is built. We devised two separate algorithms for building the network; the one we actually implemented is described here and the other is detailed in the section “Future Work”.  As implemented, the first node to enter the network becomes ultra peer 0.  If, for example, there are three nodes per ultra node, the next three nodes to connect would become node 0’s sub network.  The fifth node to join the network would become ultra node 1 and would connect to ultra node 0. In this scheme of building the network, each ultra node’s sub network is filled before the next ultra node is created.

To share files, a user must specify a share directory.  All files and sub directories in their share directory will be available to the network for download.  When a user wants to search, they enter a keyword and submit a search request.  The search request will be sent to the searching node’s ultra node.  The ultra node will send the search request to all the other peers in its sub network before broadcasting it to its connected ultra peers.  Search requests consist of four major parts - the searching node’s address, the keyword, a search id, and the time to live (ttl).  The ttl is initially set to a positive integer.  Each time a search request is passed between ultra peers, the request ttl is decremented.  Notice that ttl only limits the number of hops among ultra peers, passing a request within an ultra node and its sub network has no effect.  If an ultra node receives a search request with a ttl of 0, it will send the request to its sub network and delete the request.  If a keyword match is found, the node with the desired file sends a message to the node specified in the search request with its address and the path of the desired file relative to the share folder.  As these acknowledge messages come in to the search node, it displays to the user a list of all the files found on the network.  The user can then choose one or more files to download.  The searching node directly connects to the node with the selected file and downloads it.  The search id is sent as an attempt to significantly lessen the search request traffic on the network.  The structure of the PBJ network means there are many different paths between two ultra nodes.  While this is very useful in keeping the network stable and allowing search requests to quickly reach a large number of files, it also means that the same ultra node will receive and process a request multiple times, sending the message out to all of its ultra peers, who have already received the request.  This type of network behavior is extremely inefficient.  PBJ attempts to fix this problem in part by having a unique pair of values for each search request.  One of these values is the ultra node id the search request originated from and the other is local to each ultra node and represents the number of previous requests sent out by the ultra node.  The first request sent from ultra node 6 would have an id pair of (6,1), the second would have (6,2) etc.  Each ultra node keeps track of the last several request ids received and if the request id of a new search request matches one in the list, that request is ignored.  This scheme vastly cuts down the amount of redundant request traffic and makes the system more efficient as a whole.

An area of contention during development of PBJ was how to correctly handle ultra peer disconnection.  Various solutions were proposed, including updating the gateway, electing a node from the sub network to be a new ultra node, and the Ostrich approach (ignoring it).  We eventually decided to implement a system of letting the gateway know when an ultra node goes down.  Every time the gateway is about to add a new node to the network, it pings its ultra peers.  If one or more does not respond, it marks those as missing, and inserts ultra nodes into these positions until they are all filled, and then fills them The point here is to ensure important connections in the network are rebuilt before the ultra nodes are filled.  In addition, ultra nodes will occasionally ping their ultra peers and sub network.  If an ultra node does not get a response from an ultra peer, it removes it from the list of connected ultra peers.  If an ultra peer cannot connect to a peer in its sub network, it removes that peer from its list and notifies the gateway that a spot has opened up in its sub network.  If a node in a sub network cannot reach its ultra peer, it re enters the network through the gateway.  This ensures that all lost nodes will be replaced as new ones are added to the system, and that the network will not become fractured with high node turnover.

\section{Results}

There are a variety of improvements that PBJ could benefit from in future distributions.  One previously discussed is changing how nodes join the system.  The current gateway method functions well, but its centralized nature is hardly ideal for a system whose design so highlights decentralization.  Several alternatives have been discussed. The most likely implementation would be to place the burden of network building on the existing ultra nodes.  A node would keep track of its previously connected ultra nodes and attempt to connect to these peers.  Depending on its current status, the ultra peer might add the new users or decide to push it towards higher valued ultra peers to attempt placement.  Eventually it would either get placed in a sub network or reach the ultra peer with the highest id and become the new highest ultra peer.  If none of the previously connected nodes are currently connected to the network, a range of options could be implemented to ensure the user gets into the network including but not limited to : keeping the gateway as a backup, having ultra nodes at known URLs, placing the burden on the user to find the information.

Several different specific algorithms for how exactly the gateway builds the grid were discussed and implemented.  The basic algorithm, described above, creates a new ultra node and then fills that ultra node’s sub network before creating a new ultra peer.  While this algorithm works acceptably, it ignores several observations about PBJ’s network.  In PBJ, the number of hops it takes to get from node A to node B is highly dependent on the current number of ultra peers in the system.  As a simple example, the optimal number of hops from ultra peers 0 to 63 is 5 hops (0-16-32-48-47-63) if ultra node 64 does not exist and 2 hops (0 - 64-63) if ultra node 64 does exist.  Indeed, a node whose largest hop was one of the last nodes to be added has the optimal network structure for searching.  Our algorithm for taking advantage of this trait slightly alters how the network is built by the gateway.  The basic idea behind this algorithm is to have an ultra peer back bone in place first with empty sub networks and then fill in the sub networks.  When creating a new network, the first eight (eight is half of sixteen) nodes into the system will become the first 8 ultra peers.  The next nodes to join the system will join these ultra peers’ sub networks.  When all eight sub networks have been filled, the gateway then add the next nodes as ultra peers in the system until there are thirty two ultra peers (thirty two is half of sixty four) in the system.  This continues so that when the network is full, it grows to half the size of the next even power of 2 before filling in the ultra peers.  This ensures that the majority of the peers are close together but have the ability to move farther because there is an ultra peer structure in place to facilitate such movement. Another potential improvement would be to choose ultra peers based on network quality.  Ultra peers have to handle the vast majority of the network traffic.  It then makes sense that the machines with the strongest network connection should be ultra peers.  This would help stabilize the network and improve quality.

Simple things such as an improved GUI and security/privacy features could also be added to make the system more user friendly.  Another concern we have is attempting to mitigate is leeching, the practice where by users of a file sharing network do not share any files to be downloaded but still use the network to get files.

\section{Analysis}

\section{Conclusion}
The conclusion goes here.

% conference papers do not normally have an appendix

% use section* for acknowledgement
\section*{Acknowledgment}

The authors would like to thank...

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% that's all folks
\end{document}

### 2011-12-06 nnode.py

@@ -73,7 +73,7 @@ class Node:
 class Network:
     def __init__(self):
         print "Creating Network."
-        self.root = Node('0', True)
+        self.root = Node('A', True)
 
     def findUPeer(self, up):
         if(len(up.peers) < PEERS_PER_UPEER):
@@ -149,7 +149,7 @@ class Network:
 if __name__ == '__main__':
     # create a network and add 10 additional nodes
     n = Network()
-    names = ['A1', 'A2', 'A3', '1', 'B1', 'B2', 'B3', '2', 'C1', 'C2','C3','3','D1','D2','D3','4','E1','E2','E3','5','F1']
+    names = ['A1', 'A2', 'A3', 'B','B1', 'B2', 'B3','C','C1', 'C2', 'C3','D','D1', 'D2', 'D3','E','E1', 'E2', 'E3']
     for i in range(len(names)):
         n.newNode(names[i])   
     

### 2011-12-06 cleandeploy.sh
comments

@@ -1,4 +1,5 @@
-#!/bin/bash 
+#!/bin/bash
+#script kills all instances of python on every lab machine
 
 if [ -z "$1" ]; then
  echo "Please supply username."

### 2011-12-06 dummy.py

@@ -17,6 +17,7 @@ import httpserv
 import threading
 
 if __name__ == '__main__':
+    '''Accept share directory path as an optional argument'''
     if(len(sys.argv)==2):
         client = Client(str(sys.argv[1]))
     else:

### 2011-12-06 gateway.py

@@ -128,11 +128,13 @@ class Network:
 pbj = Network()
 @app.route("/register", methods=['GET'])
 def register():
+    '''flask method that new nodes use to register with the network'''
     data=pbj.addPeer(request.remote_addr)
     return pickle.dumps(data)
     
 @app.route("/upeer_remove_peer", methods=['POST'])
 def updatePeerCount():
+    '''flask method that ultranodes use to tell gateway they have lost a node'''
     peer=request.form['peer']
     upeer=request.remote_addr
     pbj.UPeerRemovePeer(upeer, peer)

### 2011-12-06 httpcli.py

@@ -3,7 +3,7 @@
     Adam Hodges
     Zach Welch
     
-    httpcli.py handles flask and http calls for sending information
+    httpcli.py handles http calls for sending information
 '''
 # activate virtualenv
 import os
@@ -80,13 +80,13 @@ def send_found(requestor, path):
     #print(response.read())
 
 
-def download(filename, url):
+def download(filename, url, dlpath):
     '''called by client after it has a list of results to finally download the file'''
     req=urllib2.Request(url)
     response=urllib2.urlopen(req)
     
     #write the file to the share folder
-    download = open('share/'+filename, "w")
+    download = open(dlpath+'/'+filename, "w")
     download.write(response.read())
     download.close()
     
@@ -99,12 +99,12 @@ def send_gateway_remove_peer(p):
     req=urllib2.Request(url,data)
     response=urllib2.urlopen(req)
 
-def main():
+#def main():
     #--testing functions--
-    send_search(pbj.searchReq(1,"wat.txt"), "localhost")
+    #send_search(pbj.searchReq(1,"wat.txt"), "localhost")
     #report_found(1,"hold.txt", "localhost")
     #download("hold.txt", "http://127.0.0.1:5000/share/hold.txt")
     #register("localhost")
 
-if __name__ == "__main__":
-    main()
+#if __name__ == "__main__":
+#    main()

### 2011-12-06 main.py

@@ -22,6 +22,7 @@ client = Client()
 
 class MainWindow(wx.Frame):
     def __init__(self, parent, title):
+        '''Initialize the GUI'''
         wx.Frame.__init__(self, parent, title=title, size=(500,400))
 
         # layout components
@@ -57,6 +58,7 @@ class MainWindow(wx.Frame):
         self.SetMinSize((400,300))
     
     def createSearchBar(self):
+        '''Create the search bar GUI element'''
         # Horizontal sizer
         self.searchbar = wx.BoxSizer(wx.HORIZONTAL)
 
@@ -73,18 +75,22 @@ class MainWindow(wx.Frame):
         self.searchbar.Add(self.button, 0)
 
     def search(self, event):
+        '''Function to hook button event to PBJ client instance'''
         client.search(self.inputarea.GetValue())
 
     def download(self, event):
+        '''Function to hook button event to file download'''
         if(self.resultsarea.GetSelection() != -1):
             client.download(self.resultsarea.GetString(self.resultsarea.GetSelection()))
         
     def setStatus(self, text):
+        '''Update status bar text'''
         #wx.MutexGuiEnter()
         self.SetStatusText(text)
         #wx.MutexGuiEnter()
         
     def updateResult(self, url):
+        '''Add a result to the listbox'''
         wx.MutexGuiEnter()
         self.resultsarea.Append(url)
         wx.MutexGuiLeave()

### 2011-12-06 pbj.py

@@ -43,8 +43,9 @@ class Client:
         self.share = path
 
     def __str__(self):
+        '''tostr function''''
         if(self.isUltra):
-            string = "client info:\n  Rank: Ultrapeer\n  Connected ultrapeers: %s\n  Connected peers: %s\n" % (self.upeers, self.peers)
+            string = "Client info:\n  Rank: Ultrapeer\n  Connected ultrapeers: %s\n  Connected peers: %s\n" % (self.upeers, self.peers)
         else:
             string = "Client info:\n  Rank: Peer\n  Connected ultrapeer: %s\n" % self.upeer  
         return string
@@ -149,6 +150,7 @@ class Client:
         return foundFiles
     
     def handleSearch(self, req):
+        '''gets called by flask, universal (recursive) search function'''
         #requestor is null when requestor=self
         if req.requestor is not None:
             req.ttl = req.ttl-1
@@ -201,5 +203,5 @@ class Client:
         self.handleSearch(req)
 
     def download(self, path):
-        '''download file specified by arg path'''
-        http.download(os.path.basename(path), path)
+        '''download file specified by arg path to share directory'''
+        http.download(os.path.basename(path), path, self.share)

### 2011-12-06 deploy10.sh
gateway_test for visuals (buggy)

@@ -1,0 +1,24 @@
+#!/bin/bash 
+
+if [ -z "$1" ]; then
+ echo "Please supply username."
+ exit
+fi
+
+USER=$1
+MACHINECOUNT=0
+machines=( )
+
+#10 dragons
+COUNTER=1
+while [  $COUNTER -lt 12 ]; do
+ machines[$MACHINECOUNT]=dragon$COUNTER
+ let COUNTER=COUNTER+1
+ let MACHINECOUNT=MACHINECOUNT+1
+done
+
+for machine in "${machines[@]}";
+do
+ ssh -o "StrictHostKeyChecking no" -o "ConnectTimeout=2" $USER@$machine.cs.clemson.edu "cd PBJ ; nohup ./testPBJ.sh $machine && exit" &
+ sleep 5
+done

### 2011-12-06 deploy.sh
deploy script update for demo

@@ -25,9 +25,9 @@ while [  $COUNTER -lt 28 ]; do
  let MACHINECOUNT=MACHINECOUNT+1
 done
 
-#22 geckos, but use gecko 22 as gateway
+#22 geckos, but use gecko 22 as gateway, 21 as demo
 COUNTER=1
-while [  $COUNTER -lt 22 ]; do
+while [  $COUNTER -lt 21 ]; do
  machines[$MACHINECOUNT]=gecko$COUNTER
  let COUNTER=COUNTER+1 
  let MACHINECOUNT=MACHINECOUNT+1

### 2011-12-06 dummy.py
basic comments and docstrings

@@ -1,3 +1,11 @@
+''' PBJ
+    Camden Clements
+    Adam Hodges
+    Zach Welch
+    
+    dummy.py excecutes a GUIless client, used for building a test network 
+'''
+
 # activate virtualenv
 import os, sys
 activate_this = os.path.expanduser("env/bin/activate_this.py")

### 2011-12-06 gateway.py

@@ -1,3 +1,11 @@
+''' PBJ
+    Camden Clements
+    Adam Hodges
+    Zach Welch
+    
+    gateway.py contains code for the PBJ gateway, which controls how nodes are
+    added to the network
+'''
 # activate virtualenv
 import os
 activate_this = os.path.expanduser("env/bin/activate_this.py")
@@ -19,7 +27,12 @@ app = Flask(__name__)
 PEERS_PER_UPEER = 2
 lock = threading.Lock()
 class Node:
+    '''gateway representation of a network node'''
     def __init__(self, name, ultraId):
+        '''constructor 
+           name    - IP address of node
+           ultraId - ultra peer ID number (-1 if not an ultra peer)
+        '''
         self.name = name
         if ultraId == -1:
             self.isUltra = False
@@ -31,19 +44,22 @@ class Node:
             self.upeers = {}
 
 class Network:
+    '''gateway representation of entire network'''
     def __init__(self):
+        '''constructor, sets up empty network'''
         self.upeerCount = -1
         self.upeers = {}
         self.outOfOrder = 0
 
     def findUPeer(self):
+        '''returns the ultra peer with an empty sub network slot or None if full'''
         for peer in self.upeers.values():
             if(len(peer.peers.keys()) < PEERS_PER_UPEER):
                 if self.outOfOrder == 0:                 
                     return peer
 
     def linkUPeer(self, up):
-     
+        '''links a ultra peer to all other ultra peers it should be linked with'''
         for ids,curup in self.upeers.items():
             if(up.upeerid - curup.upeerid != 0):
                 if(math.log(math.fabs((up.upeerid - curup.upeerid)), 2) % 2 == 0):
@@ -54,7 +70,10 @@ class Network:
 
   
     def addPeer(self, name):
-        print "ADDING A PEEEEEEEEEEEEEEEEEEEERR"
+        '''process for adding a peer to the network. Checks network for lost nodes
+            before adding new ones
+            name - ip address of new node to be added 
+        '''
         result = {}
         for id,up in self.upeers.items():
             if send_ping(up.name) == False:
@@ -72,7 +91,6 @@ class Network:
                 self.outOfOrder -= 1
                 for i in range(self.upeerCount):
                     if self.upeers.has_key(i) == False:
-                        print "HERE 1"
                       
                         newNode = Node(name, i)
                         self.upeers[i]= newNode
@@ -81,10 +99,6 @@ class Network:
[…]

### 2011-12-06 gateway_test.py

@@ -1,3 +1,11 @@
+''' PBJ
+    Camden Clements
+    Adam Hodges
+    Zach Welch
+    
+    gateway_test.py
+'''
+
 # activate virtualenv
 import os
 activate_this = os.path.expanduser("env/bin/activate_this.py")

### 2011-12-06 httpcli.py

@@ -1,3 +1,10 @@
+''' PBJ
+    Camden Clements
+    Adam Hodges
+    Zach Welch
+    
+    httpcli.py handles flask and http calls for sending information
+'''
 # activate virtualenv
 import os
 activate_this = os.path.expanduser("env/bin/activate_this.py")
@@ -10,8 +17,9 @@ import urllib2
 import pickle
 GATEWAY_ADDR = 'gecko22.cs.clemson.edu'
 
-#called by peer to register with ultrapeer
+
 def send_ping(node):
+    '''called by peer to register with ultrapeer'''
     url="http://"+node+":5000/ping"
     try:
         req=urllib2.Request(url)
@@ -20,15 +28,17 @@ def send_ping(node):
     except Exception:
         return False
 
-#called by node to register with gateway, returns pickle obj
+
 def send_register(gateway):
+    '''called by node to register with gateway, returns pickle obj'''
     url="http://"+gateway+":5000/register"
     req=urllib2.Request(url)
     response=urllib2.urlopen(req)
     return(response.read())
     
-#called by peer to register with ultrapeer
+
 def send_imapeer(upeer):
+    '''called by peer to register with ultrapeer'''
     url="http://"+upeer+":5000/imapeer"
     try:
         req=urllib2.Request(url)
@@ -37,8 +47,9 @@ def send_imapeer(upeer):
     except Exception:
         return False
 
-#called by ultrapeer to register with ultrapeer
+
 def send_imaupeer(upeer):
+    '''called by ultrapeer to register with another ultrapeer'''
     url="http://"+upeer+":5000/imaupeer"
     try:
         req=urllib2.Request(url)
@@ -47,8 +58,9 @@ def send_imaupeer(upeer):
     except Exception:
         return False
     
-#used to initiate/propagate a search request
+
 def send_search(searchreq, superpeerip):
+    '''used to initiate/propagate a search request'''
     url="http://"+superpeerip+":5000/search"
     values={'searchreq':pickle.dumps(searchreq)}
     
@@ -57,8 +69,9 @@ def send_search(searchreq, superpeerip):
     response=urllib2.urlopen(req)
     #print(response.read())
 
-#called by node if the file has been found
+
 def send_found(requestor, path):
+    '''called by node if the file has been found'''
     url="http://"+requestor+":5000/result"
     values={'path':path}
     data=urllib.urlencode(values)
@@ -66,8 +79,9 @@ def send_found(requestor, path):
     response=urllib2.urlopen(req)
[…]

### 2011-12-06 httpserv.py

@@ -1,3 +1,11 @@
+''' PBJ
+    Camden Clements
+    Adam Hodges
+    Zach Welch
+    
+    httpserv.py handles flask and http calls for getting information
+'''
+
 # activate virtualenv
 import os
 activate_this = os.path.expanduser("env/bin/activate_this.py")
@@ -17,10 +25,13 @@ app = Flask(__name__)
 
 app.client = None
 
-#--Node Receive Search Request--
-#Ex: curl -d "filename=wat.txt&search_id=1" http://localhost:5000/search
+
 @app.route("/search",methods=['POST'])
 def search():
+    '''
+    --Node Receive Search Request--
+    Ex: curl -d "filename=wat.txt&search_id=1" http://localhost:5000/search
+    '''
     searchreq=request.form['searchreq']
     
     searchreq=pickle.loads(str(searchreq))
@@ -34,16 +45,20 @@ def search():
 
     return searchreq.requestor + " is searching (" + str(searchreq.searchid) + ", " + searchreq.filename+")"
 
-#--Node Receive Download Request--
-#Ex: curl http://localhost:5000/share/wat.txt
 @app.route("/share/<filename>")
 def getfile(filename):
+    '''
+    --Node Receive Download Request--
+    Ex: curl http://localhost:5000/share/wat.txt
+    '''
     return send_from_directory(app.client.share,filename)
 
-#--Client Receive Search Result--
-#Ex: curl -d "path=share/wat.txt&search_id=1" http://localhost:5000/result
 @app.route("/result",methods=['POST'])
 def result():
+    '''
+    --Client Receive Search Result--
+    Ex: curl -d "path=share/wat.txt&search_id=1" http://localhost:5000/result
+    '''
     path=request.form['path']
     ip=request.remote_addr
     url="http://"+ip+":5000/share/"+path
@@ -53,24 +68,32 @@ def result():
         app.window.updateResult(url)
     return url
 
-#--UPeer Notified Of A Peer--
 @app.route("/imapeer", methods=['GET'])
 def regPeer():
-    #add request.remote_addr as a connected peer
+    '''
+    --UPeer Notified Of A Peer--
+    add request.remote_addr as a connected peer
+    '''
     app.client.addPeer(request.remote_addr)
     return "OK!"
     
-#--UPeer Notified Of Another UPeer--
+
 @app.route("/imaupeer", methods=['GET'])
 def regUPeer():
-    #add request.remote_addr as a connected upeer
[…]

### 2011-12-06 lookup.py

@@ -1,3 +1,11 @@
+''' PBJ
+    Camden Clements
+    Adam Hodges
+    Zach Welch
+    
+    lookup.py is a proof of concept for searching the share directory
+'''
+
 # activate virtualenv
 import os
 activate_this = os.path.expanduser("env/bin/activate_this.py")

### 2011-12-06 main.py

@@ -1,3 +1,11 @@
+''' PBJ
+    Camden Clements
+    Adam Hodges
+    Zach Welch
+    
+    main.py executes client code and handles GUI
+'''
+
 # activate virtualenv
 import os
 activate_this = os.path.expanduser("env/bin/activate_this.py")

### 2011-12-06 nnode.py

@@ -1,4 +1,14 @@
 # activate virtualenv
+''' PBJ
+    Camden Clements
+    Adam Hodges
+    Zach Welch
+    
+    nnode.py simulates the network being built and creates a png visualization
+    of the network. Used in designing system and algorithms
+    '''
+
+
 import os
 activate_this = os.path.expanduser("env/bin/activate_this.py")
 execfile(activate_this, dict(__file__=activate_this))

### 2011-12-06 pbj.py

@@ -1,3 +1,11 @@
+''' PBJ
+    Camden Clements
+    Adam Hodges
+    Zach Welch
+    
+    pbj.py
+'''
+
 # activate virtualenv
 import os
 activate_this = os.path.expanduser("env/bin/activate_this.py")
@@ -14,7 +22,9 @@ GATEWAY_ADDR = 'gecko22.cs.clemson.edu'
 TIME_TO_LIVE = 7
 
 class searchReq:
+    '''request for a keyword to be passed between nodes'''
     def __init__(self, searchid, filename, requestor=None):
+        '''constructor'''
         self.ttl = TIME_TO_LIVE
         self.filename = filename
         self.searchid=searchid
@@ -22,7 +32,9 @@ class searchReq:
         self.timeinit = time.time()
 
 class Client:
+    '''actual client code for node'''
     def __init__(self, path='share'):
+        '''constructor'''
         self.isUltra = None     # boolean
         self.peers = []   # list of connected peers
         self.upeers = []  # list of connected ultrapeers
@@ -39,6 +51,7 @@ class Client:
         return string
 
     def getUpeers(self):
+        '''return connected ultra peers'''
         if(self.isUltra):
             upeers=self.upeers
         else:
@@ -67,6 +80,7 @@ class Client:
         t.start()    
 
     def reconnect(self):
+        '''reconnect to gateway after lost ultrapeer'''
         self.isUltra = None     # boolean
         self.peers = []   # list of connected peers
         self.upeers = []  # list of connected ultrapeers
@@ -91,6 +105,9 @@ class Client:
                 self.reconnect()
 
     def pingNodes(self):
+        '''ping all connected ultra peers and sub peers, removing them if no reply.
+            if self is not an ultrapeer, reconnect to gateway if lost ultrapeer
+        '''
         while True:
             time.sleep(5)
             print("tick")
@@ -118,6 +135,7 @@ class Client:
                     self.reconnect()
 
     def checkForFile(self,filename):
+        '''search for a file in the share directory'''
         foundFiles = []
         for root, dirs, files in os.walk(self.share):
             for name in files:
@@ -159,6 +177,7 @@ class Client:
                 http.send_search(req, self.upeer)
 
     def addPeer(self, p):
+        '''add a peer to an ultra node'''
         print("adding peer "+ p)
         if self.peers is None:
             self.peers=[p]
@@ -166,6 +185,7 @@ class Client:
             self.peers.append(p)
     
[…]

### 2011-12-06 virtualenv.py

@@ -1,3 +1,11 @@
+''' PBJ
+    Camden Clements
+    Adam Hodges
+    Zach Welch
+    
+    virtualenv.py
+'''
+
 import os, sys
 
 os.system("virtualenv env")

### 2011-12-06 gateway.py
added comments to gateway, removed flags cause it don't work

@@ -11,7 +11,6 @@ import os
 activate_this = os.path.expanduser("env/bin/activate_this.py")
 execfile(activate_this, dict(__file__=activate_this))
 
-#import socket
 import pickle
 import sys
 import math
@@ -25,7 +24,7 @@ from httpcli import send_ping
 app = Flask(__name__)
 
 PEERS_PER_UPEER = 2
-lock = threading.Lock()
+
 class Node:
     '''gateway representation of a network node'''
     def __init__(self, name, ultraId):
@@ -52,7 +51,7 @@ class Network:
         self.outOfOrder = 0
 
     def findUPeer(self):
-        '''returns the ultra peer with an empty sub network slot or None if full'''
+        '''returns the ultra peer with an empty sub network slot or None if all ultra peers are full'''
         for peer in self.upeers.values():
             if(len(peer.peers.keys()) < PEERS_PER_UPEER):
                 if self.outOfOrder == 0:                 
@@ -66,8 +65,6 @@ class Network:
                     print "Linking ultrapeers %d and %d." % (curup.upeerid, up.upeerid)
                     up.upeers[curup.name] = curup
                     curup.upeers[up.name] = up
-
-
   
     def addPeer(self, name):
         '''process for adding a peer to the network. Checks network for lost nodes
@@ -75,6 +72,8 @@ class Network:
             name - ip address of new node to be added 
         '''
         result = {}
+
+        # ping ultrapeers to verify network
         for id,up in self.upeers.items():
             if send_ping(up.name) == False:
                 print "Lost Ultrapeer ", id
@@ -82,23 +81,24 @@ class Network:
                 self.outOfOrder += 1
                 self.upeerCount -= 1
 
-
         upeer = self.findUPeer()
         if upeer is None:
+            # new peer is ultra peer
             result['isUltra'] = True
             self.upeerCount += 1
+            
+            # adjust ultrapeers
             if  self.outOfOrder != 0:
                 self.outOfOrder -= 1
                 for i in range(self.upeerCount):
                     if self.upeers.has_key(i) == False:
-                      
                         newNode = Node(name, i)
                         self.upeers[i]= newNode
                         self.linkUPeer(newNode)
                         result['uPeers'] = newNode.upeers.keys()
                         print "Node %s added to network as Ultrapeer %d." % (name, newNode.upeerid)
-
[…]

### 2011-12-06 pbj.py
commented pbj.. could probably use some cleaning

@@ -15,7 +15,6 @@ import pickle
 import time
 import threading
 
-#from httpcli import send_register, send_search, send_imapeer, send_imaupeer, send_found, send_ping, send_gateway_remove_peer
 import httpcli as http
 
 GATEWAY_ADDR = 'gecko22.cs.clemson.edu'
@@ -59,19 +58,23 @@ class Client:
         return upeers
 
     def connectToNetwork(self):
+        '''Establish connectiong with gateway and process result'''
         data = http.send_register(GATEWAY_ADDR)
         data = pickle.loads(data)
-        nodesToPing=()
 
         if data['isUltra']:
+            # node is an ultrapeer
             self.isUltra = True
             self.upeers = data['uPeers']
+            # connect to listed ultrapeers
             if self.upeers is not None:
                 for up in self.upeers:
                     http.send_imaupeer(up)
         else:
+            # node is not ultrapeer
             self.isUltra = False
             self.upeer = data['uPeer']
+            # connect to listed ultrapeer
             if http.send_imapeer(self.upeer) is False:
                 time.sleep(5)
                 self.reconnect()
@@ -89,7 +92,7 @@ class Client:
         self.completedSearches = {}
         data = http.send_register(GATEWAY_ADDR)
         data = pickle.loads(data)
-        nodesToPing=()
+
         if data['isUltra']:
             self.isUltra = True
             if data['uPeers'] is not None:
@@ -192,9 +195,11 @@ class Client:
             self.upeers.append(up)
 
     def search(self, filename):
+        '''create search request for filename'''
         req=searchReq(self.searchctr, filename)
         self.searchctr=self.searchctr+1
         self.handleSearch(req)
 
     def download(self, path):
+        '''download file specified by arg path'''
         http.download(os.path.basename(path), path)

### 2011-12-06 main.py
added comments to main. modified readme

@@ -89,14 +89,6 @@ class MainWindow(wx.Frame):
         self.resultsarea.Append(url)
         wx.MutexGuiLeave()
 
-#class runWindow(threading.Thread):
-#    def __init__(self, app):
-#        threading.Thread.__init__(self)
-#        self.app = app
-#    def run(self):
-#        print "here"
-#        self.app.MainLoop()
-
 class runClient(threading.Thread):
     def __init__(self, client, frame):
         threading.Thread.__init__(self)
@@ -110,11 +102,10 @@ def main():
     frame = MainWindow(None, "PBJ")
     client.connectToNetwork()
     frame.setStatus("Connected to " + str(client.getUpeers()))
-    #t=runWindow(app)
-    #t.start()
+
     c = runClient(client, frame)
     c.start()
-    #httpserv.run(client, frame)
+  
     app.MainLoop()
 
 if __name__ == '__main__':

### 2011-12-08 paper/paper.tex
paper

\documentclass[conference]{IEEEtran}

\hyphenation{op-tical net-works semi-conduc-tor}

\usepackage{xcolor,graphicx}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{PBJ: A Gnutella Inspired File Sharing System }

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Camden Clements}
\IEEEauthorblockA{School of Computing\\
Clemson University\\
Clemson, SC 29632\\
Email: camdenc@gmail.com}
\and
\IEEEauthorblockN{Adam Hodges}
\IEEEauthorblockA{School of Computing\\
Clemson University\\
Clemson, SC 29632\\
Email: hodges8@clemson.edu}
\and
\IEEEauthorblockN{Zach Welch}
\IEEEauthorblockA{School of Computing\\
Clemson University\\
Clemson, SC 29632\\
Email: zwelch@clemson.edu}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% make the title area
\maketitle

\begin{abstract}
\boldmath
PBJ is a distributed file sharing system designed on many of the same principles of the gnutella file sharing application.  Rather than route search requests through some central entity like Napster and, to a lesser extent, BitTorrent, PBJ creates a network of connected users.  Search requests are broadcast between users and files are downloaded directly between them.  This paper details the algorithms behind PBJ, the specifics of its implementation, and a comparison of PBJ to other popular file sharing systems.  Future improvements to PBJ are also discussed.

\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}

Peer to peer (P2P) file sharing applications are some of the most well known and ubiquitous distributed systems today. These applications allow users of their system to share and download files between each other (usually) free of charge.  In the last fifteen years, file sharing has gone from virtually nonexistent to one of the largest sources of Internet traffic [SOURCE].  P2P system structure can vary wildly from highly centralized, in which a single server handles all requests, to highly decentralized, where there are no central elements and the user client programs work together to find results. Beyond basic topology, there are a host of design trade offs.  We were also interested in creating a system that would not be considered liable if illegal content were shared on it. This has been a problem for file sharing applications in the past, particularly Napster. PBJ is a distributed file system that has been designed to be stable, reliable, and able to adapt to changing needs of its users. Due to these design goals, we decided to loosely base the design of PBJ on Gnutella, a highly distributed file sharing application. While our overall design is Gnutella based, we looked at a range of famous file sharing systems, and several of them influenced our decision making during the design process. 
\subsection{Background}

\subsubsection{Napster}
A defining characteristic of a P2P file sharing application is the kind of network topology it employs.  Napster, one of the first file sharing networks, was a highly centralized system.  All  online Napster users connected to a central server.  Each user would have a folder designated for sharing audio files (only mp3s were transferred on Napster).  This central server would handle a user request by searching for related files in the share folders of other users.  The central server would then report a list of relevant files and their locations that the user could choose to download.  Any files the requesting user chose to download would directly connect with the associated machine for actual file transfer. The ability to search for and download music free of charge was very popular and the Napster user base was very large.  It also happened that a large percentage of the downloads on Napster constituted copyright infringement, since users were distributing music without the creator’s consent. From a legal standpoint, the flaw in Napster’s design was that all of the files on the system were indexed on the central server, including files that broke copyright.  This meant that legally, Napster knew about and facilitated copyright infringement.  In 2001, when the inevitable flood of copyright infringement lawsuits were filed against Napster, a court order shut down the central server.  Because it is a central server, the network ceases to exist when it is taken down. File sharing applications developed after Napster’s shut down attempted to avoid legal liability by making their applications less centralized and by not having their computers keep track of individual files.  \subsubsection{BitTorrent}
 With the dismantling of Napster, file sharing applications started to become more complex and decentralized. Most file sharing today involves the BitTorrent protocol.  BitTorrent differs from other file sharing systems in that it downloads file segments from multiple sources instead of a single file transfer between two users.  BitTorrent works by having a user obtain a torrent file (usually by downloading it from a website).  The local BitTorrent client interprets the contents of the torrent file and connects with a tracker, a server with information about how to find the file. The tracker finds seeders, other BitTorrent clients, with a local copy of the file to be transferred. The file also identifies the swarm, a set of clients with a portion of the file, usually in the process of downloading it themselves.  The searching client downloads from these sources simultaneously to build the desired file.  BitTorrent is especially useful for downloading popular files, since there will be a large pool of seeders and a large swarm.  While BitTorrent is clearly more distributed than Napster, since there are multiple central servers instead of a single large server for the entire application.  However, if the tracker(s) in a torrent file are taken down, there is no way that torrent file can be used to obtain the actual file.        \subsubsection{Gnutella}
Gnutella (a portmanteau of GNU, the free software project, and Nutella, the chocolate and hazelnut spread) is a decentralized network of interconnected users running a gnutella client called a node.  Search requests are broadcast to all of the searching node’s neighbor clients (which gnutella terms “peers”), which in turn broadcast the request to all of their peers as well.  This goes on until the file is found or the request goes a specified number of peer hops without finding a file (much like the time to live field in an IP packet). A list of the files that match the search are displayed to the user, who then chooses the file to download. The searching node connects directly to the node with the desired file for file transfer. This hop based searching algorithm does allow for the possibility that a search request may fail to return a file in the network, especially as the network gets larger and larger.  Later versions of gnutella’s network introduced the concept of ultra nodes and ultra peers. Each ultra node is connected to a network of regular nodes as well as a large number of other ultra nodes, each having its own network of nodes, making gnutella a network of networks.  The reason for this change is that it allows many more nodes to be reached from any one node in a smaller number of hops, making searching more efficient and the system more scalable.  Nodes keep track of the other nodes they have previously connected with and attempt to reconnect to the network through these nodes.  When connecting for the first time, these nodes must attempt to connect a set of nodes guaranteed to be in the gnutella network.  This means that despite the highly decentralized nature of gnutella, a few centralized elements remain to facilitate the bootstrapping process.  Unlike Napster, which kept information about files on company machines, gnutella does not keep track of the files transferred on their system.  This means that they are not liable if copyright infringement occurs on their system.

\section{Methodology}
PBJ takes the key qualities of gnutella and uses them only as a starting point, rather than implementing a version of the actual gnutella protocol. Lessons learned from looking at applications like Napster and BitTorrent also played a role in the design of PBJ.  PBJ functions like gnutella in that it creates a network of connected user nodes.  However, it also borrows an important idea from Napster (though slightly altered).  PBJ has a central server running called the gateway.  While Napster kept track of files stored on the system, the gateway keeps track of the nodes in the system and controls the building of the network.  The gateway allows for easy handling of stabilizing the network with nodes being added and removed regularly from the system.  There are three things the PBJ network is designed to handle : building the network, searching the network, and handling node disconnects.  \subsection{Building the Network}
 LIke gnutella, PBJ contains a network of ultra nodes. Each of these ultra nodes has a set of nodes that form an ultra node’s sub network. Ultra nodes in PBJ are given a unique ID starting at 0 and increasing by one each time a new ultra node is added to the network. An ultra node’s ID is assigned in the gateway when it is added to the network. This unique ID is a vital element to building the network.

 \begin{figure}[tbh]
\centering
\includegraphics[width=0.5\textwidth]{362prez}
\caption{PBJ Network of Ultra Peers}
\end{figure}
The basic algorithm for connecting ultra nodes in the network builds an outward spiral of ultra peers.  While this alone would be wildly inefficient in terms of searching and stability, new ultra nodes also connect to ultra nodes deeper within the spiral.  This allows search requests to quickly move between otherwise distant ultra nodes. More specifically, the first ultra node created will be given an ID of 0, the second an ID of 1, etc.  When an ultra node is created with ID Y, it will attempt to connect to all nodes $X, 0 < X < Y$, where $\log_2 (|Y - X|) = Z , Z$ being an even integer.  So for example, node 16 would connect with node 15 $(16 - 15 = 1 = 2^0)$, node 12 $(16 - 12 = 4 = 2^2)$, and node 0 $(16 - 0 = 16 = 2^4)$.

A clear benefit of this structure is that the PBJ network has a high level of redundancy in the connections.  This means that the nodes are connected in such a way that it is easy for search requests to reach most, if not all, of the nodes on the network in a few hops.  Currently, the process of actually adding ultra peers to the network and telling them which other ultra peers to connect to is handled through the gateway. The main job of the gateway is to make decisions about how to add a new user node to the network. The gateway keeps track of the status of all the ultrapeers currently in the system.  When a new node tries to join the system, the gateway makes several decisions based on the current status of the PBJ network.  First, the gateway decides if the new node will become an ultra node.  If so, it will give the new ultra node a list of other ultra nodes to connect to.  If the new node is not an ultra node, the gateway will provide information on the appropriate ultra peer sub network to join. These decisions by the gateway essentially dictate how the network is built. We devised two separate algorithms for building the network; the one we actually implemented is described here and the other is detailed in the section “Future Work”.  As implemented, the first node to enter the network becomes ultra node 0.  If, for example, there are three nodes per ultra node, the next three nodes to connect would become node 0’s sub network.  The fifth node to join the network would become ultra node 1 and would connect to ultra node 0. In this scheme of building the network, each ultra node’s sub network is filled before the next ultra node is created.  This algorithm ensures that the graph has the smallest number of ultra nodes possible in a system and all but potentially the last ultra node have filled sub networks.

\subsection{Searching the Network}

The PBJ client allows a share path to be passed as a command line argument. The default share directory is a subdirectory named “share”. All files and sub directories in the user’s share directory will be available to the network for other nodes to download.  When a user wants to search, they enter a keyword and submit a search request.  The search request will be sent to the searching node’s ultra node (unless the node is itself an ultra node).
\begin{figure}[tbh]
\centering
\includegraphics[width=0.5\textwidth]{search}
\caption{Searching For a File}
\end{figure}

 The ultra node will send the search request to all of the other peers in its sub network before broadcasting it to its connected ultra peers.  Search requests consist of four major parts - the searching node’s address, the keyword, a search id, and the time to live (ttl).  The ttl is initially set to a positive integer.  Each time a search request is passed between ultra peers, the request ttl is decremented.  Notice that ttl only limits the number of hops among ultra peers, passing a request within an ultra node and its sub network has no effect.  If an ultra node receives a search request with a ttl of 0, it will send the request to its sub network and delete the request.  If the keyword is found in any part of a filename, the finding node sends a message to the search node with its IP address and the path of the desired file relative to the share folder.  As these acknowledgement messages come into the search node, it displays to the user a list of all the files found on the network.  The user can then choose one or more of the files to download.  The searching node directly connects to the node with the selected file and downloads it.

 The search ID was added as part of the search request as an attempt to significantly lessen the search request traffic on the network.  The structure of the PBJ network means there are many different paths between any two ultra nodes.  While this is very useful in keeping the network stable and allowing search requests to quickly reach a large number of files, it also means that the same ultra node will receive and process a request multiple times, sending the message out to all of its ultra peers, who have already received the request.  This type of network behavior is extremely inefficient.  PBJ attempts to fix this problem in part by having a unique pair of values in each search request.  One of these values is the IP address of the requester and the other is a search ID that is local to each node and represents the number of requests previously sent out by that node. Together, this (address, search ID) pair make a unique request identifier. Each node keeps track of the last several request ID pairs received and if the request ID pair of a newly received search request matches one in the list, that request is ignored.  This scheme vastly cuts down the amount of redundant request traffic and makes the system more efficient as a whole.     
\subsection{Disconnecting from the Network}
An area of contention during development of PBJ was how to correctly handle ultra peer disconnection.  Various solutions were proposed, including updating the gateway, electing a node from the sub network to be a new ultra node, and the Ostrich approach (ignoring it).  We eventually decided to implement a system of having the gateway check on existing ultra nodes.  Upon receiving a request to add a new node to the network, the gateway pings every ultra node in the network. If one or more does not respond, the gateway marks those as missing, and inserts ultra nodes into these positions until they are all filled. The point here is to ensure that important connections in the network are rebuilt before attempting to refill the sub networks of ultra nodes. In addition, ultra nodes will occasionally ping their ultra peers and sub network.  If an ultra node does not get a response from an ultra peer, it removes it from the list of connected ultra peers.  If an ultra peer cannot connect to a peer in its sub network, it removes that peer from its list and notifies the gateway that a spot has opened up in its sub network.  If a node in a sub network cannot reach its ultra peer, it re enters the network through the gateway.  This ensures that all lost nodes will be replaced as new ones are added to the system, and that the network will not become fractured with high node turnover.

\section{Results}
All of the PBJ network communication is facilitated through the use of the Flask python module. Flask is a web microframework that is designed to simplify the development of Python web applications. HTTP was chosen as a protocol over TCP due to its reliability, simplicity, and flexibility. Flask trivializes the implementation of custom HTTP responses. Every node, as well as the gateway, is running an instance of a Flask server. The server is configured to run on port 5000 as a default, but this could be easily changed.
Flask was not available as an installed Python module on the lab machines that we were planning on using for our testing, and we did not have administrative privileges to install it, so we needed a way in which we could install and use Flask on every lab machine without modifying any system files. The solution was to use virtualenv, which is a tool used to create virtual Python environments. A virtual Python environment can be created in a users home folder on a system using virtualenv, and then that user has permission to modify that environment however they wish. In this way, we were able to deploy a Python environment with the Flask module and its dependencies installed on every lab machine.

A concern of ours when laying out the specification of how nodes would communicate was the case in which a node would have to communicate across a firewall. Firewalls add a great deal of complexity when designing a distributed system that is intended to be accessed by a large number of computers under diverse network constraints. Our ultimate decision was that since our project is academic in nature and limited in resources, we were going to ignore the cases in which communication over port 5000 is unavailable to a node.

\subsection{Test Plan}
In order to claim that we have designed a stable and scalable system with confidence, we needed to design a solid testing plan. In the design phase of our project, we thoroughly discussed the use of Condor, a HTC application that can deploy processes to a large number of computers, to test our network stability and search algorithms for large numbers of nodes. Unfortunately, the computers on Clemson’s Condor network are equipped with Windows Firewall, which blocks the access of ports that have not been explicitly granted permission. As previously discussed, we will be ignoring the cases in which our nodes are behind firewalls, so this test strategy was inadequate. Instead, we devised a test strategy in which we wrote a script to connect every available lab machine we had to our network.

The end result was a test environment in which over 70 search-able nodes with unique files were connected to our network. Although this is a considerable amount of nodes, we found that it was not sufficient to fully test the scaling and performance of our search algorithm. We used this large network of connected nodes primarily to test the functionality and reliability of our system.
The main goals of testing the gateway server was twofold. First, correct network topology was to be maintained when new nodes were added.  This could easily be checked by feeding the gateway a large number of pseudo nodes to verify that the intended topology could be maintained for any size network. Furthermore, an applet was developed to display an image representing the network graph, making it easier to see node to node connections. The second goal of gateway testing was to verify that any dropped node notifications were being handled correctly, which involved updating the network structure for addition of future nodes. This is further discussed later when testing node functions.

Testing node functionality proved to be much more in depth. For this, we developed a series of repeatable test cases that the network should be able to handle. These test cases included: initiating a search as an ultra node, initiating a search as a node, searching from one end of the network to the other, searching from the middle of the network to either end, and downloading a search result. We also monitored the gateway to ensure that the network structure was maintained and rebuilt after all node disconnection scenarios: dropping a node from the beginning, middle, and end of the network, as well as dropping an ultra node from the beginning, middle, and end of the network.
We repeated these test cases after every change we made to ensure that PBJ was stable and working properly.
\section{Analysis}

Our testing demonstrated to us the stability of the network. To a large extent, the main goals of the project were met. A network of connected peers could be created using only a simple centralized gateway, while keeping file searching and downloading independent of such a server. We discovered, however, that there was a large amount of traffic on the network between the pinging of peers and redundant searching, even reduced as it is with the unique request ID. We also feel that an explicit ttl will eventually limit PBJ’s scalability. This section provides an in depth look at our test results and possible improvements future versions of our system could implement to deal with these perceived issues.

\subsection{Future Work}

\subsubsection{Decentralization}
One improvement previously discussed is changing how nodes join the system. The current gateway method functions well, but its centralized nature is hardly ideal for a system whose design so highlights decentralization. Several alternatives have been discussed. The most likely implementation would be to place the burden of network building on the existing ultra nodes.  A node would keep track of its previously connected ultra nodes and attempt to connect to these peers. Depending on its current status, the ultra peer might add the new users or decide to push it towards higher valued ultra peers to attempt placement. Eventually it would either get placed in a sub network or reach the ultra peer with the highest id and become the new highest ultra peer.  If none of the previously connected nodes are currently connected to the network, a range of options could be implemented to ensure the user gets into the network including but not limited to: keeping the gateway as a backup, having ultra nodes at known URLs, placing the burden on the user to find the information.

\subsubsection{Network topology}
Several different specific algorithms for how exactly the network is organized were discussed. The current algorithm, described above, creates a new ultra node and then fills that ultra node’s sub network before creating a new ultra peer. While this algorithm works acceptably, it ignores several observations about PBJ’s network. In PBJ, the number of hops it takes to get from node A to node B is highly dependent on the current number of ultra peers in the system. As a simple example, the optimal number of hops from ultra peers 0 to 63 is 5 hops (0-16-32-48-47-63) if ultra node 64 does not exist and 2 hops (0 -64-63) if ultra node 64 does exist. Indeed, a node whose largest hop was one of the last nodes to be added has the optimal network structure for searching.

 Our algorithm for taking advantage of this trait slightly alters how the network is built by the gateway. The basic idea behind this algorithm is to have an ultra peer back bone in place first with empty sub networks and then fill in the sub networks. When creating a new network, the first eight (eight is half of sixteen) nodes into the system will become the first eight ultra peers. The next nodes to join the system will join these ultra peers’ sub networks. When all eight sub networks have been filled, the gateway then add the next nodes as ultra peers in the system until there are thirty-two ultra peers (thirty two is half of sixty four) in the system. This continues so that when the network is full, it grows to half the size of the next even power of two before filling in the ultra peers. This ensures that the majority of the peers are close together but have the ability to move farther because there is an ultra peer structure in place to facilitate such movement.  Another potential improvement would be to choose ultra peers based on network quality. Ultra peers have to handle the vast majority of the network traffic. It then makes sense that the machines with the strongest network connection should be ultra peers. This would help stabilize the network and improve quality.

\subsubsection{Searching}
We also feel the search algorithm could be improved or a new algorithm implemented. Going forward, it seems that the ttl is the main issue to be addressed. Its purpose is to limit system traffic, but if the network becomes large enough, it is possible searches from a certain node will never reach other machines far enough away in the network. Though additional testing would be necessary, we would need to see the effects of larger ttl values on system traffic. It may make sense to remove the ttl all together and count on the unique ID checking to limit redundant network traffic. We have also discussed tiers of ttl values corresponding to the size of the hop to be taken. This algorithm is still early in development and would need more research.

\subsubsection{Stabilization}
Handling node failure was a tough challenge in early development. As convenient and stabilizing as our node ping method for detecting disconnected nodes is to the network, it leads to a lot of network traffic. Currently, nodes ping each other every few seconds. It might make sense to have nodes ping only right before sending a search request, or to implement some kind of TCP style application level three way hand shake. In addition, it might make sense for ultra nodes to contact the gateway when they have lost contact with an ultra peer, rather than having the gateway ping all ultra nodes in the network.

\subsubsection{User experience}
Simple things such as an improved GUI and security/privacy features could also be added to make the system more user friendly. Another concern we have is attempting to mitigate is leeching, the practice where by users of a file sharing network do not share any files to be downloaded but still use the network to get files.

\section{Conclusion}

PBJ is a decentralized file sharing system whose highly connected nodes, search algorithm, and intelligent node loss handling make the ground work for a stable and reliable application. PBJ is heavily influenced by existing file sharing services gnutella and to a much lesser extent Napster. PBJ users connect to the system through a dedicated gateway, either becoming ultra nodes connected to other ultra nodes or part of an ultra node’s sub network. Searching the network is done by keyword comparison to filenames, and search requests are broadcast between ultra peers.

 Results are displayed to the user to choose a result to download. The gateway and the nodes themselves periodically ping their connections. If an ultra peer does not respond to a ping, it is removed from the ultra node’s active connections.  If a sub network node’s ultra node does not respond, the node will exit the network and attempt to reconnect through the gateway. Every time the gateway attempts add a node, it first checks that existing ultra peers are connected.  If one has gone down, the node to be added is added in that ultra peer’s place. PBJ uses Flask for network communication.

Thorough unit testing of both gateway server and node application functions proved the functionality of the PBJ network. It also let us see what areas of the sharing system need the most attention in order to improve performance. Network scalability and stability were seen to be correct and fully functional as intended.
Based on this testing, however, we have a number of future improvements to PBJ.  These improvements would increase the network’s stability, decrease redundant traffic, and reach a larger percentage of the network.

% conference papers do not normally have an appendix

% use section* for acknowledgement
\section*{Acknowledgment}

The authors would like to thank Dr. Goasguen for his help and advice, the Clemson University Systems staff for quickly responding to the various technical problems and hurdles faced in setting up machines for testing, and Dunkin Donuts for making their delicious coffee the authors used in the majority of this project.

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% that's all folks
\end{document}

### 2011-12-08 nnode.py

@@ -83,7 +83,7 @@ class Node:
 class Network:
     def __init__(self):
         print "Creating Network."
-        self.root = Node('A', True)
+        self.root = Node('0', True)
 
     def findUPeer(self, up):
         if(len(up.peers) < PEERS_PER_UPEER):
@@ -159,7 +159,7 @@ class Network:
 if __name__ == '__main__':
     # create a network and add 10 additional nodes
     n = Network()
-    names = ['A1', 'A2', 'A3', 'B','B1', 'B2', 'B3','C','C1', 'C2', 'C3','D','D1', 'D2', 'D3','E','E1', 'E2', 'E3']
+    names = ['0-1', '0-2', '0-3', '1','1-1', '1-2', '1-3','2','2-1', '2-2', '2-3','3','3-1', '3-2', '3-3','4','4-1', '4-2', '4-3']
     for i in range(len(names)):
         n.newNode(names[i])   
     

### 2011-12-08 paper/paper.tex
more paper

@@
 These applications allow users of their system to share and download files between each other (usually) free of charge.
-In the last fifteen years, file sharing has gone from virtually nonexistent to one of the largest sources of Internet traffic [SOURCE].
+In the last fifteen years, file sharing has gone from virtually nonexistent to one of the largest sources of Internet traffic ~\cite{study}.
 P2P system structure can vary wildly from highly centralized, in which a single server handles all requests, to highly decentralized, where there are no central elements and the user client programs work together to find results.
@@
 PBJ is a distributed file system that has been designed to be stable, reliable, and able to adapt to changing needs of its users.
-Due to these design goals, we decided to loosely base the design of PBJ on Gnutella, a highly distributed file sharing application.
-While our overall design is Gnutella based, we looked at a range of famous file sharing systems, and several of them influenced our decision making during the design process.
+Due to these design goals, we decided to loosely base the design of PBJ on gnutella, a highly distributed file sharing application.
+While our overall design is gnutella based, we looked at a range of famous file sharing systems, and several of them influenced our decision making during the design process.
 \subsection{Background}
@@
 File sharing applications developed after Napster’s shut down attempted to avoid legal liability by making their applications less centralized and by not having their computers keep track of individual files.
+Napster exists today as a subscription based service ~\cite{napster}
   \subsubsection{BitTorrent}
  With the dismantling of Napster, file sharing applications started to become more complex and decentralized.
-Most file sharing today involves the BitTorrent protocol.
+Most file sharing today involves the BitTorrent protocol ~\cite{bit}.
 BitTorrent differs from other file sharing systems in that it downloads file segments from multiple sources instead of a single file transfer between two users.
@@
 Gnutella (a portmanteau of GNU, the free software project, and Nutella, the chocolate and hazelnut spread) is a decentralized network of interconnected users running a gnutella client called a node.
-Search requests are broadcast to all of the searching node’s neighbor clients (which gnutella terms “peers”), which in turn broadcast the request to all of their peers as well.
+Search requests are broadcast to all of the searching node’s neighbor clients (which gnutella terms “peers”), which in turn broadcast the request to all of their peers as well ~\cite{lookup}.
 This goes on until the file is found or the request goes a specified number of peer hops without finding a file (much like the time to live field in an IP packet).
@@
 This hop based searching algorithm does allow for the possibility that a search request may fail to return a file in the network, especially as the network gets larger and larger.
-Later versions of gnutella’s network introduced the concept of ultra nodes and ultra peers.
+Later versions of gnutella’s network introduced the concept of ultra nodes and ultra peers ~\cite{evo}.
 Each ultra node is connected to a network of regular nodes as well as a large number of other ultra nodes, each having its own network of nodes, making gnutella a network of networks.
@@
 All of the PBJ network communication is facilitated through the use of the Flask python module.
-Flask is a web microframework that is designed to simplify the development of Python web applications.
+Flask ~\cite{flask} is a web microframework that is designed to simplify the development of Python web applications.
 HTTP was chosen as a protocol over TCP due to its reliability, simplicity, and flexibility.
@@
 Flask was not available as an installed Python module on the lab machines that we were planning on using for our testing, and we did not have administrative privileges to install it, so we needed a way in which we could install and use Flask on every lab machine without modifying any system files.
-The solution was to use virtualenv, which is a tool used to create virtual Python environments.
+The solution was to use virtualenv ~\cite{virtual}, which is a tool used to create virtual Python environments.
 A virtual Python environment can be created in a users home folder on a system using virtualenv, and then that user has permission to modify that environment however they wish.
@@
 % (used to reserve space for the reference number labels box)
-\begin{thebibliography}{1}
+\begin{thebibliography}{9}
 
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
+\bibitem{evo}
+Amir H. Rasti, Daniel Stutzach, Reza Rejaie, "On the Long term Evolution of the Two Tier Gnutella Overlay", in \emph{INFOCOM Proceedings}, Barcelona, Spain, 2006, pp 1 - 6
+\bibitem{napster}
+Napster Website: http://www.napster.com
+\bibitem{bit}
+BitTorrent Website: http://www.bittorrent.com/
+\bibitem{compare}
+Dimitrios Tsoumakos and Nick Roussopoulos. (2011, 11, 20) "A comparison of Peer to Peer Search Methods" [Online]. Available : Google Scholar
+\bibitem{flask}
+Flask Website : http://flask.pocoo.org/
+\bibitem{virtual}
+Virtualenv Website : http://www.virtualenv.org/en/latest/index.html
+\bibitem{lookup}
+Hari Balakrishnan et al, "Looking Up Data in P2P Systems". \emph{Communications of the ACM}, vol 46, No 3,  February, 2003.
+\bibitem{study}
+Hendrik Schuleze and Klaus Mochalski. "Internet Study 2008/2009". Ipoque Leipzig Germany, 2009
 \end{thebibliography}

### 2011-12-17 dummy.py
dsf

@@ -13,8 +13,16 @@ execfile(activate_this, dict(__file__=activate_this))
 
 from pbj import Client
 import httpserv
-
+import csv
 import threading
+import time
+
+class dummyClass:
+    def __init__(self):
+        self.csvwriter=csv.writer(open("results.csv", "wb"))
+
+    def updateResult(self, url, searchresult):
+        csvwriter.writerow([searchresult.searchid, searchresult.timeinit, time.time(), searchrequest.ttl, searchrequest.lastUltranode, url])
 
 if __name__ == '__main__':
     '''Accept share directory path as an optional argument'''
@@ -22,6 +30,8 @@ if __name__ == '__main__':
         client = Client(str(sys.argv[1]))
     else:
         client = Client()
+        dummy = dummyClass()
+
     client.connectToNetwork()
-    httpserv.run(client)
+    httpserv.run(client, obsDummy=dummy)
 

### 2011-12-17 gateway.py

@@ -96,6 +96,7 @@ class Network:
                         self.upeers[i]= newNode
                         self.linkUPeer(newNode)
                         result['uPeers'] = newNode.upeers.keys()
+                        result['upId'] = newNode.upeerid
                         print "Node %s added to network as Ultrapeer %d." % (name, newNode.upeerid)
                         return result
             # put new upeer at end of upeers
@@ -103,6 +104,7 @@ class Network:
             self.upeers[self.upeerCount]= newNode
             self.linkUPeer(newNode)
             result['uPeers'] = newNode.upeers.keys()
+            result['upId'] = newNode.upeerid
             print "Node %s added to network as Ultrapeer %d." % (name, newNode.upeerid)
 
             return result

### 2011-12-17 httpcli.py

@@ -15,7 +15,7 @@ execfile(activate_this, dict(__file__=activate_this))
 import urllib
 import urllib2
 import pickle
-GATEWAY_ADDR = 'gecko22.cs.clemson.edu'
+GATEWAY_ADDR = '10.125.5.149'
 
 
 def send_ping(node):
@@ -70,10 +70,11 @@ def send_search(searchreq, superpeerip):
     #print(response.read())
 
 
-def send_found(requestor, path):
+def send_found(requestor, path, searchreq):
     '''called by node if the file has been found'''
     url="http://"+requestor+":5000/result"
-    values={'path':path}
+    values={'path':path, 'searchreq':pickle.dumps(searchreq)}
+
     data=urllib.urlencode(values)
     req=urllib2.Request(url,data)
     response=urllib2.urlopen(req)

### 2011-12-17 httpserv.py

@@ -25,6 +25,11 @@ app = Flask(__name__)
 
 app.client = None
 
+@app.route("/tellsearch",methods=['POST'])
+def tellsearch():
+    searchterm=request.form['searchterm']
+    app.client.search(searchterm)
+    return "ok"
 
 @app.route("/search",methods=['POST'])
 def search():
@@ -59,6 +64,9 @@ def result():
     --Client Receive Search Result--
     Ex: curl -d "path=share/wat.txt&search_id=1" http://localhost:5000/result
     '''
+    searchreq=request.form['searchreq']
+    searchreq=pickle.loads(str(searchreq))
+
     path=request.form['path']
     ip=request.remote_addr
     url="http://"+ip+":5000/share/"+path
@@ -66,6 +74,9 @@ def result():
     
     if(app.window is not None):
         app.window.updateResult(url)
+    if(app.dummy is not None):
+        app.dummy.updateResult(url, searchreq)
+
     return url
 
 @app.route("/imapeer", methods=['GET'])
@@ -96,11 +107,12 @@ def ping():
     '''
     return "OK!"
 
-def run(obsClient, obsWindow=None):
+def run(obsClient, obsWindow=None, obsDummy=None):
     import logging
     hdlr=logging.FileHandler('flask.log')
     app.logger.addHandler(hdlr)
     app.client=obsClient
     app.window=obsWindow
+    app.dummy=obsDummy
     app.run(host='0.0.0.0')
     

### 2011-12-17 pbj.py

@@ -17,7 +17,7 @@ import threading
 
 import httpcli as http
 
-GATEWAY_ADDR = '10.125.5.249'
+GATEWAY_ADDR = '10.125.5.149'
 TIME_TO_LIVE = 7
 
 class searchReq:
@@ -29,12 +29,14 @@ class searchReq:
         self.searchid=searchid
         self.requestor=requestor
         self.timeinit = time.time()
+        self.lastUltranode = None
 
 class Client:
     '''actual client code for node'''
     def __init__(self, path='share'):
         '''constructor'''
         self.isUltra = None     # boolean
+        self.upId = None
         self.peers = []   # list of connected peers
         self.upeers = []  # list of connected ultrapeers
         self.upeer = None # ultrapeer of node
@@ -66,6 +68,7 @@ class Client:
         if data['isUltra']:
             # node is an ultrapeer
             self.isUltra = True
+            self.upId = data['upId']
             self.upeers = data['uPeers']
             # connect to listed ultrapeers
             if self.upeers is not None:
@@ -96,6 +99,7 @@ class Client:
 
         if data['isUltra']:
             self.isUltra = True
+            self.upId=data['upId']
             if data['uPeers'] is not None:
                 self.upeers = data['uPeers']
             if self.upeers is not None:
@@ -114,27 +118,19 @@ class Client:
         '''
         while True:
             time.sleep(5)
-            print("tick")
             if(self.isUltra):
                 if self.upeers is not None:
-                    print("iterating through upeers")
                     for up in self.upeers:
-                        print("pinging upeer "+up)
                         if(http.send_ping(up) is False):
-                            print("up "+ up + " disconnected")
                             self.upeers.remove(up)
                 if self.peers is not None:
-                    print("iterating through peers " + str(self.peers))
                     for p in self.peers:
-                        print("pinging peer "+p)
                         if(http.send_ping(p) is False):
-                            print("p " + p + " disconnected")
                             self.peers.remove(p)
                             http.send_gateway_remove_peer(p)
                             #update gateway peer count
             else:
                 if(http.send_ping(self.upeer) is False):
-                    print("Lost connection to upeer "+self.upeer+", reconnecting to network.")
                     time.sleep(5)
                     self.reconnect()
 
@@ -152,6 +148,9 @@ class Client:
     def handleSearch(self, req):
         '''gets called by flask, universal (recursive) search function'''
[…]

### 2011-12-17 dummy.py
gfh

@@ -29,13 +29,9 @@ if __name__ == '__main__':
     if(len(sys.argv)==2):
         client = Client(str(sys.argv[1]), '5000')
     else:
-<<<<<<< HEAD
-        client = Client()
+        client = Client('share', '5000')
         dummy = dummyClass()
 
-=======
-        client = Client('share', '5000')
->>>>>>> 5af39263551bfb04248beba3077370bbe2c50b7c
     client.connectToNetwork()
     httpserv.run(client, obsDummy=dummy)
 

### 2011-12-17 httpcli.py

@@ -70,18 +70,12 @@ def send_search(searchreq, superpeerip):
     #print(response.read())
 
 
-<<<<<<< HEAD
-def send_found(requestor, path, searchreq):
-    '''called by node if the file has been found'''
-    url="http://"+requestor+":5000/result"
-    values={'path':path, 'searchreq':pickle.dumps(searchreq)}
 
-=======
 def send_found(port, request):
     '''called by node if the file has been found'''
     url="http://"+request.requestor+":"+request.requestorport+"/result"
     values={'result':pickle.dumps(request), 'port':port}
->>>>>>> 5af39263551bfb04248beba3077370bbe2c50b7c
+
     data=urllib.urlencode(values)
     req=urllib2.Request(url,data)
     response=urllib2.urlopen(req)

### 2011-12-17 httpserv.py

@@ -64,17 +64,11 @@ def result():
     --Client Receive Search Result--
     Ex: curl -d "path=share/wat.txt&search_id=1" http://localhost:5000/result
     '''
-<<<<<<< HEAD
-    searchreq=request.form['searchreq']
-    searchreq=pickle.loads(str(searchreq))
 
-    path=request.form['path']
-=======
     result = request.form['result']
     result = pickle.loads(str(result))
     path = result.path
-    print "%i hops this time." % result.hops
->>>>>>> 5af39263551bfb04248beba3077370bbe2c50b7c
+
     ip=request.remote_addr
     url="http://"+ip+":"+request.form['port']+"/share/"+path
     #add url/ip to list of results
@@ -82,7 +76,7 @@ def result():
     if(app.window is not None):
         app.window.updateResult(url)
     if(app.dummy is not None):
-        app.dummy.updateResult(url, searchreq)
+        app.dummy.updateResult(url, result)
 
     return url
 
@@ -120,10 +114,6 @@ def run(obsClient, obsWindow=None, obsDummy=None):
     app.logger.addHandler(hdlr)
     app.client=obsClient
     app.window=obsWindow
-<<<<<<< HEAD
     app.dummy=obsDummy
-    app.run(host='0.0.0.0')
-=======
-    app.run(host='0.0.0.0', port=obsClient.port)
->>>>>>> 5af39263551bfb04248beba3077370bbe2c50b7c
+    app.run(host='0.0.0.0',port=obsClient.port)
     

### 2011-12-17 pbj.py

@@ -17,11 +17,7 @@ import threading
 
 import httpcli as http
 
-<<<<<<< HEAD
 GATEWAY_ADDR = '10.125.5.149'
-=======
-GATEWAY_ADDR = 'gecko22.cs.clemson.edu'
->>>>>>> 5af39263551bfb04248beba3077370bbe2c50b7c
 TIME_TO_LIVE = 7
 
 class searchReq:
@@ -34,11 +30,8 @@ class searchReq:
         self.requestor=None
         self.requestorport=port
         self.timeinit = time.time()
-<<<<<<< HEAD
         self.lastUltranode = None
-=======
         self.hops = 0
->>>>>>> 5af39263551bfb04248beba3077370bbe2c50b7c
 
 class Client:
     '''actual client code for node'''
@@ -162,7 +155,7 @@ class Client:
             if(req.requestor not in self.completedSearches):
                 self.completedSearches[req.requestor]=[]
 
-            if (req.searchid in self.completedSearches[req.requestor]) or req.ttl<=0:
+            if (req.searchid in self.completedSearches[req.requestor]): #or req.ttl<=0:
                 return
 
             self.completedSearches[req.requestor].append(req.searchid)

### 2011-12-17 dummy.py
first results

@@ -16,21 +16,32 @@ import httpserv
 import csv
 import threading
 import time
+import socket
 
 class dummyClass:
-    def __init__(self):
-        self.csvwriter=csv.writer(open("results.csv", "wb"))
-
+    def __init__(self, path):
+        self.csvfile=path+'.csv'
     def updateResult(self, url, searchresult):
-        csvwriter.writerow([searchresult.searchid, searchresult.timeinit, time.time(), searchrequest.ttl, searchrequest.lastUltranode, url])
+        file=open(self.csvfile, "at")
+        self.csvwriter=csv.writer(file)
+        self.csvwriter.writerow([searchresult.searchid, searchresult.timeinit, time.time(), searchresult.ttl, searchresult.lastUltranode, url])
+        file.close()
 
 if __name__ == '__main__':
     '''Accept share directory path as an optional argument'''
+    sock = socket.socket(socket.AF_INET, socket.SOCK_STREAM)
+    sock.bind(('localhost', 0))
+    port = sock.getsockname()[1]
+    sock.close()
+
+    port = str(port)
+
     if(len(sys.argv)==2):
-        client = Client(str(sys.argv[1]), '5000')
+        client = Client(str(sys.argv[1]), port)
     else:
-        client = Client('share', '5000')
-        dummy = dummyClass()
+        client = Client('share', port)
+
+    dummy = dummyClass(str(sys.argv[1]))
 
     client.connectToNetwork()
     httpserv.run(client, obsDummy=dummy)

### 2011-12-17 gateway.py

@@ -20,10 +20,10 @@ import argparse
 
 from flask import Flask
 from flask import request
-from httpcli import send_ping
+from httpcli import send_ping, send_tellsearch
 app = Flask(__name__)
 
-PEERS_PER_UPEER = 2
+PEERS_PER_UPEER = 0
 
 class Node:
     '''gateway representation of a network node'''
@@ -77,7 +77,7 @@ class Network:
 
         # ping ultrapeers to verify network
         for id,up in self.upeers.items():
-            if send_ping(up.name up.port) == False:
+            if send_ping(up.name) == False:
                 print "Lost Ultrapeer ", id
                 del self.upeers[id]
                 self.outOfOrder += 1
@@ -88,6 +88,10 @@ class Network:
             # new peer is ultra peer
             result['isUltra'] = True
             self.upeerCount += 1
+
+            if(self.upeerCount>1):
+                print "Telling " + self.upeers[0].name + " to search"
+                send_tellsearch("", self.upeers[0].name)
             
             # adjust ultrapeers
             if  self.outOfOrder != 0:

### 2011-12-17 httpcli.py

@@ -57,7 +57,14 @@ def send_imaupeer(myport, upeer):
         return True
     except Exception:
         return False
-    
+
+def send_tellsearch(searchterm, peer):
+    url="http://"+peer+"/tellsearch"
+    values={'searchterm':searchterm}
+    data=urllib.urlencode(values)
+    req=urllib2.Request(url,data)
+    response=urllib2.urlopen(req)
+
 
 def send_search(searchreq, superpeerip):
     '''used to initiate/propagate a search request'''

### 2011-12-17 pbj.py

@@ -136,10 +136,11 @@ class Client:
         foundFiles = []
         for root, dirs, files in os.walk(self.share):
             for name in files:
-                if name.lower().find(filename.lower()) != -1:
-                    newFile = root + '/' + name
-                    prev,split,post = newFile.partition(self.share+'/')
-                    foundFiles.append(post)
+                if name != "results.csv":
+                    if name.lower().find(filename.lower()) != -1:
+                        newFile = root + '/' + name
+                        prev,split,post = newFile.partition(self.share+'/')
+                        foundFiles.append(post)
         return foundFiles
     
     def handleSearch(self, req):

### 2011-12-17 dummy.py
results 2

@@ -24,7 +24,7 @@ class dummyClass:
     def updateResult(self, url, searchresult):
         file=open(self.csvfile, "at")
         self.csvwriter=csv.writer(file)
-        self.csvwriter.writerow([searchresult.searchid, searchresult.timeinit, time.time(), searchresult.ttl, searchresult.lastUltranode, url])
+        self.csvwriter.writerow([searchresult.searchid, searchresult.timeinit, time.time(), searchresult.hops, searchresult.lastUltranode, url])
         file.close()
 
 if __name__ == '__main__':

### 2011-12-17 pbj.py
results 4

@@ -170,12 +170,14 @@ class Client:
         if(self.isUltra):
             if self.peers is not None:
                 for p in self.peers:
-                    http.send_search(req, p)
+                    if p is not req.requestor:
+                        http.send_search(req, p)
             
             if self.upeers is not None:    
                 for up in self.upeers:
-                    #http.send req to connected upeer
-                    http.send_search(req, up)
+                    if up is not req.requestor:
+                        #http.send req to connected upeer
+                        http.send_search(req, up)
         else:
             if self.upeer is not req.requestor:
                 http.send_search(req, self.upeer)

### 2011-12-17 pbj.py
results 5

@@ -149,17 +149,20 @@ class Client:
         if(self.isUltra):
             req.lastUltranode=self.upId
 
+        requestorname=""
         if req.requestor is not None:
             req.ttl = req.ttl-1
             req.hops = req.hops+1
 
-            if(req.requestor not in self.completedSearches):
-                self.completedSearches[req.requestor]=[]
+            requestorname=req.requestor+":"+req.requestorport
 
-            if (req.searchid in self.completedSearches[req.requestor]): #or req.ttl<=0:
+            if(requestorname not in self.completedSearches):
+                self.completedSearches[requestorname]=[]
+
+            if (req.searchid in self.completedSearches[requestorname]): #or req.ttl<=0:
                 return
 
-            self.completedSearches[req.requestor].append(req.searchid)
+            self.completedSearches[requestorname].append(req.searchid)
                 
             for foundFile in self.checkForFile(req.filename):
                 #found file
@@ -170,16 +173,16 @@ class Client:
         if(self.isUltra):
             if self.peers is not None:
                 for p in self.peers:
-                    if p is not req.requestor:
+                    if p != requestorname:
                         http.send_search(req, p)
             
             if self.upeers is not None:    
                 for up in self.upeers:
-                    if up is not req.requestor:
+                    if up != requestorname:
                         #http.send req to connected upeer
                         http.send_search(req, up)
         else:
-            if self.upeer is not req.requestor:
+            if self.upeer != requestorname:
                 http.send_search(req, self.upeer)
 
     def addPeer(self, p):

### 2011-12-19 paper/paper.tex
add csv data parser

@@
-\documentclass[conference]{IEEEtran}
+\documentclass{acm_proc_article-sp}
 
@@
 \usepackage{xcolor,graphicx}
-
+\usepackage{verbatim} 
 \begin{document}
@@
 % affiliations
-\author{\IEEEauthorblockN{Camden Clements}
-\IEEEauthorblockA{School of Computing\\
-Clemson University\\
-Clemson, SC 29632\\
-Email: camdenc@gmail.com}
-\and
-\IEEEauthorblockN{Adam Hodges}
-\IEEEauthorblockA{School of Computing\\
-Clemson University\\
-Clemson, SC 29632\\
-Email: hodges8@clemson.edu}
-\and
-\IEEEauthorblockN{Zach Welch}
-\IEEEauthorblockA{School of Computing\\
-Clemson University\\
-Clemson, SC 29632\\
-Email: zwelch@clemson.edu}}
-
+\numberofauthors{3}
+\author{
+\alignauthor
+Camden Clements\\
+       \affaddr{School of Computing}\\
+       \affaddr{Clemson University}\\
+       \affaddr{Clemson, SC 29632}\\
+       \email{camdenc@gmail.com}
+\alignauthor
+Adam Hodges\\
+       \affaddr{School of Computing}\\
+       \affaddr{Clemson University}\\
+       \affaddr{Clemson, SC 29632}\\
+       \email{hodges8@clemson.edu}
+\alignauthor
+Zach Welch\\
+       \affaddr{School of Computing}\\
+       \affaddr{Clemson University}\\
+       \affaddr{Clemson, SC 29632}\\
+       \email{zwelch@clemson.edu}
+}
 % conference papers do not typically use \thanks and this command
@@
 \boldmath
-PBJ is a distributed file sharing system designed on many of the same principles of the gnutella file sharing application.
-Rather than route search requests through some central entity like Napster and, to a lesser extent, BitTorrent, PBJ creates a network of connected users.
+A common basis of differentiating peer to peer (P2P) file sharing applications is by their degree of reliance on a central server.
+Some applications, like Napster, rely completely on a central server for organizing users and searching for files.
+This kind of structure simplifies system organization and ensures constant time searching.
+It also places the burden of the entire system on the server and server failure leads to a total loss of functionality.
+Other applications, like gnutella, have no central node, instead connecting users together and passing search requests between users.
+This removes the chance of system failure from loss of a single entity, but complicates the network and makes searching less efficient.
+
+PBJ (Please Be Jenerous) is a file sharing application designed to marry the positive aspects of the centralized and decentralized paradigms.
+PBJ users are connected to each other to form a network of users, and requests are passed among them.
+To connect users to the system, PBJ uses a central gateway as a simple, powerful way to control the way the network is built to optimize the network.
+The PBJ gateway allows for increased network stability and efficiency, and if the gateway should go down, existing users can function without it.
+
+\begin{comment}{
+ PBJ is based on many of the same principles of the gnutella file sharing application.
+Rather than route search requests through some central entity like Napster, PBJ creates a network of connected users.
 Search requests are broadcast between users and files are downloaded directly between them.
@@
 Future improvements to PBJ are also discussed.
-
+\end{comment}
 \end{abstract}
@@
 % creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
 
@@
 While our overall design is gnutella based, we looked at a range of famous file sharing systems, and several of them influenced our decision making during the design process.
-\subsection{Background}
 
-\subsubsection{Napster}
+\section{Related Work}
+\subsection{Napster}
 A defining characteristic of a P2P file sharing application is the kind of network topology it employs.
@@
 Any files the requesting user chose to download would directly connect with the associated machine for actual file transfer.
+Because a given node has only to contact the central server, lookup in Napster can be done in constant time.
+~\cite{superpeer}
+
 The ability to search for and download music free of charge was very popular and the Napster user base was very large.
@@
 Napster exists today as a subscription based service ~\cite{napster}
-  \subsubsection{BitTorrent}
+\begin{comment}
+  \subsection{BitTorrent}
  With the dismantling of Napster, file sharing applications started to become more complex and decentralized.
@@
 However, if the tracker(s) in a torrent file are taken down, there is no way that torrent file can be used to obtain the actual file.
-\subsubsection{Gnutella}
+ \end{comment}
+
+   \subsection{Gnutella}
 Gnutella (a portmanteau of GNU, the free software project, and Nutella, the chocolate and hazelnut spread) is a decentralized network of interconnected users running a gnutella client called a node.
 Search requests are broadcast to all of the searching node’s neighbor clients (which gnutella terms “peers”), which in turn broadcast the request to all of their peers as well ~\cite{lookup}.
-This goes on until the file is found or the request goes a specified number of peer hops without finding a file (much like the time to live field in an IP packet).
+Lookup in gnutella is $O(log n)$ where $n$ is the number of peers in the system.~\cite{super peer} This goes on until the file is found or the request goes a specified number of peer hops without finding a file (much like the time to live field in an IP packet).
 A list of the files that match the search are displayed to the user, who then chooses the file to download.
@@
 % (used to reserve space for the reference number labels box)
-\begin{thebibliography}{9}
+\begin{thebibliography}{99}
 
@@
 Hendrik Schuleze and Klaus Mochalski. "Internet Study 2008/2009". Ipoque Leipzig Germany, 2009
+\bibitem{superpeer}
+Alper Tugay Misrak et al. "Structured Superpeers: Leveraging Heterogeneity to Provide Constant-Time Lookup" . \emph{WIAPP 2003 Proceedings}
+\bibitem{saroiu}
+S. Saroiu, P. Gummadi, S. D. Gribble,  \emph{A Measurement Study of Peer-to-Peer File Sharing Systems}, 
+University of Washington Technical Report UW-CSE-01-06-02, July 2001.
+\bibitem{adar}
+Eytan Adar , Bernardo A. Huberman. " Free Riding on Gnutella". 2000
+
 \end{thebibliography}

### 2011-12-19 resultsParse.py

@@ -1,0 +1,58 @@
+'''
+takes in a raw results csv with format
+    searchid,init time, final time,numHops,lastUpeer,url
+and produces a csv file with format
+searchid,avgTime,MaxTime,avgHops,MaxHops,MaxHopsUP
+    with filename p + rawdataname
+
+
+'''
+
+import os,sys
+import csv
+
+
+class datum:
+    def __init__(self,time,hops,hopUP):
+        self.maxTime = time
+        self.maxHops = hops
+        self.maxUP = hopUP
+        self.num = 1
+        self.sumTime = time
+        self.sumHops = hops
+    def add(self,time,hops,hopUP):
+        self.sumTime = self.sumTime + time
+        self.sumHops = self.sumHops + hops
+        self.num = self.num + 1
+        if time > self.maxTime:
+            self.maxTime = time
+        if hops > self.maxHops:
+            self.maxHops = hops
+            self.maxUP = hopUP
+    def compute(self):
+        self.avgTime = self.sumTime / self.num
+        self.avgHops = float(self.sumHops) / self.num
+        
+
+
+file = csv.reader(open(sys.argv[1],"r"))
+data = {}
+for row in file:
+    if data.has_key(row[0]):
+        data[row[0]].add(float(row[2]) - float(row[1]),int(row[3]),int(row[4]))
+    else:
+        data[row[0]] = datum(float(row[2]) - float(row[1]),int(row[3]),int(row[4]))
+    
+outFile = open('p'+sys.argv[1], "wt")
+outWriter = csv.writer(outFile)
+
+for key,item in data.items():
+    item.compute()
+    outWriter.writerow([key,item.avgTime,item.maxTime,item.avgHops,item.maxHops,item.maxUP])
+
+outFile.close()
+
+
+
+
+

### 2011-12-19 httpcli.py
results 7 (300 nodes)

@@ -15,7 +15,7 @@ execfile(activate_this, dict(__file__=activate_this))
 import urllib
 import urllib2
 import pickle
-GATEWAY_ADDR = '10.125.5.149'
+GATEWAY_ADDR = '10.125.3.145'
 
 
 def send_ping(node):

### 2011-12-19 pbj.py

@@ -17,7 +17,7 @@ import threading
 
 import httpcli as http
 
-GATEWAY_ADDR = '10.125.5.149'
+GATEWAY_ADDR = '10.125.3.145'
 TIME_TO_LIVE = 7
 
 class searchReq:

### 2011-12-21 paper/paper.tex
some analysis

@@
 
+\begin{figure}[tbh]
+\centering
+\includegraphics[width=0.5\textwidth]{searchTime}
+\caption{Search Time to Reach All Nodes in a Network}
+\end{figure}
+
+\begin{figure}[tbh]
+\centering
+\includegraphics[width=0.5\textwidth]{hops}
+\caption{Number of Hops to Reach All Nodes in a Network}
+\end{figure}
+
+Our results show that there is a high correlation between network structure and the number of hops required to reach all the nodes on the system.
+Looking at the average number of hops to reach every ultra peer in a network, several trends become apparent.
+First, every time a ultra peer with an even power of two connects to ultra peer 0, (ultra peers 4, 16, 64, and 256) the average number of hops to traverse the network decreases by approximately one hop.
+Once this drop has occurred, as new ultra peers are added to the network, the average number of hops grows at a roughly linear rate to about one more hop on average than the previous peak.
+Notice that the slope between peaks is decreasing with an increasing number of nodes.
+This implies that as PBJ gets more and more ultra peers, the addition of ultra peers will have less of an impact on average number of hops to find a file.
+
+The data for the maximum number of hops to traverse the network seems to imply that a pre defined ttl would quickly limit the ability of the network to find files in the system.
+Initially, the maximum number of hops is very unstable, with large changes between a few ultra peers.
+As ultra peers are added to the network the maximum number of hops needed to reach a node in the network seems to fall into a step function, with long stretches of no change.
+
 \subsection{Future Work}

### 2011-12-21 paper/paper.tex
more paper

@@
 
+The search time results show a positive linear trend with some obvious noise distortion.
+Many of the spikes in search time are likely due to network latency.
+When ultra node 0 reaches its next connection with ultra node 256, both the average and total search time become much less volitile, likely due to the fact that far fewer hops are now required to reach the highest ultra peers.
+These numbers represent an idle network where the only messages being passed are search requests from ultra node 0.
+In actual use, there would be many messages concurrently, so it is likely that search times would be higher than shown here.
+Since the majority of this time depends on the latency of the network and the ability of ultra peers to handle large numbers of search requests, an ideal configuration would have the users with the strongest network connections serve as ultra peers.
+Several studies have shown that taking advantage of the underlying structure of the physical network can lead to better search times in gnutella ~\cite{Ripeanu}.
+A similar approach here would be beneficial.
+
 \begin{figure}[tbh]
@@
 Eytan Adar , Bernardo A. Huberman. " Free Riding on Gnutella". 2000
+\bibitem{Ripeanu}
+Matei Ripeanu, Adriana Iamnitchi, Ian Foster. "Mapping the Gnutella Network". \emph{IEEE Internet Computing}, January-February 2002.
 

### 2012-01-05 paper/paper.tex
updated testing section

@@
 Beyond basic topology, there are a host of design trade offs.
-We were also interested in creating a system that would not be considered liable if illegal content were shared on it.
+We were interested in creating a system that would not be considered liable if illegal content were shared on it.
 This has been a problem for file sharing applications in the past, particularly Napster.
@@
 Napster, one of the first file sharing networks, was a highly centralized system.
-All  online Napster users connected to a central server.
+All Napster users connected to a central server.
 Each user would have a folder designated for sharing audio files (only mp3s were transferred on Napster).
@@
 \end{figure}
-The basic algorithm for connecting ultra nodes in the network builds an outward spiral of ultra peers.
+The basic algorithm for connecting ultra nodes in the network can be visualized as an outward spiral of ultra peers.
 While this alone would be wildly inefficient in terms of searching and stability, new ultra nodes also connect to ultra nodes deeper within the spiral.
@@
 If so, it will give the new ultra node a list of other ultra nodes to connect to.
-If the new node is not an ultra node, the gateway will provide information on the appropriate ultra peer sub network to join.
+If the new node is not an ultra node, the gateway will provide information on the appropriate ultra node sub network to join.
 These decisions by the gateway essentially dictate how the network is built.
@@
 Every node, as well as the gateway, is running an instance of a Flask server.
-The server is configured to run on port 5000 as a default, but this could be easily changed.
-Flask was not available as an installed Python module on the lab machines that we were planning on using for our testing, and we did not have administrative privileges to install it, so we needed a way in which we could install and use Flask on every lab machine without modifying any system files.
+The instance of the Flask server is told to use on a random port that is not currently in use.
+Flask was not available as an installed Python module on the machines that we were planning on using for our testing, and we did not have administrative privileges to install it, so we needed a way in which we could install and use Flask on every lab machine without modifying any system files.
 The solution was to use virtualenv ~\cite{virtual}, which is a tool used to create virtual Python environments.
@@
 Firewalls add a great deal of complexity when designing a distributed system that is intended to be accessed by a large number of computers under diverse network constraints.
-Our ultimate decision was that since our project is academic in nature and limited in resources, we were going to ignore the cases in which communication over port 5000 is unavailable to a node.
+Our ultimate decision was that since our project is academic in nature and limited in resources, we were going to ignore the cases in which communication over the allocated port is unavailable to a node.
 
@@
 As previously discussed, we will be ignoring the cases in which our nodes are behind firewalls, so this test strategy was inadequate.
-Instead, we devised a test strategy in which we wrote a script to connect every available lab machine we had to our network.
+Instead, we requested and were granted permission to perform our testing on Clemson's Palmetto cluster.
+Our account on the cluser utilized a shared network drive between nodes, so we had to write a script that would create a unique share file in a unique share directory.
+Each node was to have a single shared file for consistency.
+The end result was a test environment in which 300 search-able nodes with unique files were connected to our network.
 
-The end result was a test environment in which over 70 search-able nodes with unique files were connected to our network.
-Although this is a considerable amount of nodes, we found that it was not sufficient to fully test the scaling and performance of our search algorithm.
-We used this large network of connected nodes primarily to test the functionality and reliability of our system.
+We decided to focus our testing on the search performance and scalability of our network structure.
+To do this, we eliminated the sub networks so that every new node was designated as an ultra node.
+We also added additional functionality to the nodes to allow the gateway to tell a node to initiate a search.
+We designated ultra node 0 to be the searching node for our testing.
+The gateway was modified so that it initiated a search from node 0 upon the addition of a new node to the network.
+Node 0 then was to log the time the search took for each result, as well as how many hops the request made until each result was found.
+Nodes were added to the network at intervals of one second, which gave us 300 test results that describe the scalability of our system.
+
+%can we remove this paragraph? its pretty much fluff/no longer relevant
+%but i would feel bad deleting a whole paragraph without consulting
 The main goals of testing the gateway server was twofold.
@@
 
+%our we going to talk about our other "testing" or just the palmetto stuff? if the latter, del this too
 Testing node functionality proved to be much more in depth.
@@
 Looking at the average number of hops to reach every ultra peer in a network, several trends become apparent.
-First, every time a ultra peer with an even power of two connects to ultra peer 0, (ultra peers 4, 16, 64, and 256) the average number of hops to traverse the network decreases by approximately one hop.
+First, every time an ultra peer with an even power of two connects to ultra peer 0, (ultra peers 4, 16, 64, and 256) the average number of hops to traverse the network decreases by approximately one hop.
 Once this drop has occurred, as new ultra peers are added to the network, the average number of hops grows at a roughly linear rate to about one more hop on average than the previous peak.

### 2012-01-10 paper/paper.tex
PAPERZ

@@
 \boldmath
-A common basis of differentiating peer to peer (P2P) file sharing applications is by their degree of reliance on a central server.
+A common basis of differentiating peer to peer (P2P) file sharing applications is by their degree of centralization, or how reliant the application is on a single central element.
 Some applications, like Napster, rely completely on a central server for organizing users and searching for files.
@@
 This removes the chance of system failure from loss of a single entity, but complicates the network and makes searching less efficient.
+The design decisions apparent in these applications affect virtually every aspect of their functionality and stability.
 
@@
 
-Peer to peer (P2P) file sharing applications are some of the most well known and ubiquitous distributed systems today.
-These applications allow users of their system to share and download files between each other (usually) free of charge.
-In the last fifteen years, file sharing has gone from virtually nonexistent to one of the largest sources of Internet traffic ~\cite{study}.
-P2P system structure can vary wildly from highly centralized, in which a single server handles all requests, to highly decentralized, where there are no central elements and the user client programs work together to find results.
-Beyond basic topology, there are a host of design trade offs.
-We were interested in creating a system that would not be considered liable if illegal content were shared on it.
-This has been a problem for file sharing applications in the past, particularly Napster.
+Peer to peer (P2P) file sharing applications are some of the most well known and ubiquitous distributed systems in existance.
+These applications allow users to share and download files between each other, often free of charge.
+Since its inception in the 1990s, peer to peer file sharing has grown into one of the largest sources of Internet traffic ~\cite{study}.
+One of the defining characteristics of a P2P system is how users find files.
+P2P system structure can range from highly centralized, in which a single server handles all search requests, to highly decentralized, where there are no central elements and the user client programs work together to find results.
+Centralized applications tend to offer faster, absolute results at the expense of system stability while decentralized applications sacrifice speed for a network with no single critical element.
+Beyond this basic topology, there are a host of design trade offs that also affect the system.
+
 PBJ is a distributed file system that has been designed to be stable, reliable, and able to adapt to changing needs of its users.
 Due to these design goals, we decided to loosely base the design of PBJ on gnutella, a highly distributed file sharing application.
+In creating PBJ, we were also interested in creating a system that  would not be considered liable if illegal content were shared on it.
+This has been a problem for file sharing applications in the past, particularly Napster.
 While our overall design is gnutella based, we looked at a range of famous file sharing systems, and several of them influenced our decision making during the design process.
@@
 Any files the requesting user chose to download would directly connect with the associated machine for actual file transfer.
-Because a given node has only to contact the central server, lookup in Napster can be done in constant time.
+Because a given node has only to contact the central server, look-up in Napster can be done in constant time.
 ~\cite{superpeer}
 
-The ability to search for and download music free of charge was very popular and the Napster user base was very large.
-It also happened that a large percentage of the downloads on Napster constituted copyright infringement, since users were distributing music without the creator’s consent.
+The ability to search for and download music free of charge was very popular and the Napster user base grew very large in the late 1990s and early 2000s.
+It also happened that a large percentage of the downloads on Napster constituted copyright infringement, since users were distributing copyrighted music without the creator’s consent.
 From a legal standpoint, the flaw in Napster’s design was that all of the files on the system were indexed on the central server, including files that broke copyright.
 This meant that legally, Napster knew about and facilitated copyright infringement.
-In 2001, when the inevitable flood of copyright infringement lawsuits were filed against Napster, a court order shut down the central server.
-Because it is a central server, the network ceases to exist when it is taken down.
-File sharing applications developed after Napster’s shut down attempted to avoid legal liability by making their applications less centralized and by not having their computers keep track of individual files.
+In 2001, when the inevitable flood of lawsuits were filed against Napster, a court order shut down the central server.
+Because Napster was a centralized application, the network ceased to exist when the server was taken down.
+File sharing applications developed after Napster’s shut down attempted to avoid legal liability by making their applications less centralized and by not having any centralized elements keep track of individual files.
 Napster exists today as a subscription based service ~\cite{napster}
@@
 Gnutella (a portmanteau of GNU, the free software project, and Nutella, the chocolate and hazelnut spread) is a decentralized network of interconnected users running a gnutella client called a node.
-Search requests are broadcast to all of the searching node’s neighbor clients (which gnutella terms “peers”), which in turn broadcast the request to all of their peers as well ~\cite{lookup}.
-Lookup in gnutella is $O(log n)$ where $n$ is the number of peers in the system.~\cite{super peer} This goes on until the file is found or the request goes a specified number of peer hops without finding a file (much like the time to live field in an IP packet).
+Search requests are broadcast to all of the searching node’s neighbor clients (which gnutella terms ‘peers’), which in turn broadcast the request to all of their peers as well ~\cite{lookup}.
+Look-up in gnutella is $O(log n)$ where $n$ is the number of peers in the system.~\cite{super peer} This goes on until the file is found or the request goes a specified number of peer hops without finding a file (much like the time to live field in an IP packet).
 A list of the files that match the search are displayed to the user, who then chooses the file to download.
@@
 \section{Methodology}
-PBJ takes the key qualities of gnutella and uses them only as a starting point, rather than implementing a version of the actual gnutella protocol.
+PBJ takes key design qualities of gnutella and uses them only as a starting point, rather than implementing a version of the actual gnutella protocol.
 Lessons learned from looking at applications like Napster and BitTorrent also played a role in the design of PBJ.
@@
 There are three things the PBJ network is designed to handle : building the network, searching the network, and handling node disconnects.
+
 \subsection{Building the Network}
- LIke gnutella, PBJ contains a network of ultra nodes.
+ Like gnutella, PBJ contains a network of ultra nodes.
 Each of these ultra nodes has a set of nodes that form an ultra node’s sub network.
 Ultra nodes in PBJ are given a unique ID starting at 0 and increasing by one each time a new ultra node is added to the network.
-An ultra node’s ID is assigned in the gateway when it is added to the network.
+An ultra node's ID is assigned in the gateway when it is added to the network.
 This unique ID is a vital element to building the network.
@@
 These decisions by the gateway essentially dictate how the network is built.
-We devised two separate algorithms for building the network; the one we actually implemented is described here and the other is detailed in the section “Future Work”.
+We devised two separate algorithms for building the network; the one we actually implemented is described here and the other is detailed in the section ‘Future Work’.
 As implemented, the first node to enter the network becomes ultra node 0.
@@
 The PBJ client allows a share path to be passed as a command line argument.
-The default share directory is a subdirectory named “share”.
-All files and sub directories in the user’s share directory will be available to the network for other nodes to download.
+The default share directory is a sub-directory named ‘share’.
+All files and sub directories in the userÕs share directory will be available to the network for other nodes to download.
 When a user wants to search, they enter a keyword and submit a search request.
-The search request will be sent to the searching node’s ultra node (unless the node is itself an ultra node).
+The search request will be sent to the searching nodeÕs ultra node (unless the node is itself an ultra node).
 \begin{figure}[tbh]
@@
 
-\section{Results}
+\section{Implementation}
 All of the PBJ network communication is facilitated through the use of the Flask python module.
-Flask ~\cite{flask} is a web microframework that is designed to simplify the development of Python web applications.
+Flask ~\cite{flask} is a web micro-framework that is designed to simplify the development of Python web applications.
 HTTP was chosen as a protocol over TCP due to its reliability, simplicity, and flexibility.
@@
 The instance of the Flask server is told to use on a random port that is not currently in use.
-Flask was not available as an installed Python module on the machines that we were planning on using for our testing, and we did not have administrative privileges to install it, so we needed a way in which we could install and use Flask on every lab machine without modifying any system files.
-The solution was to use virtualenv ~\cite{virtual}, which is a tool used to create virtual Python environments.
+Flask was not available as an installed Python module on the machines that we used testing, and we lacked administrative privileges to install it.
+To install and use Flask on every lab machine without modifying any system files, PBJ uses virtualenv ~\cite{virtual}, which is a tool used to create virtual Python environments.
 A virtual Python environment can be created in a users home folder on a system using virtualenv, and then that user has permission to modify that environment however they wish.
-In this way, we were able to deploy a Python environment with the Flask module and its dependencies installed on every lab machine.
+In this way, we were able to deploy a Python environment with the Flask module and its dependencies installed on every machine running PBJ.
 
-A concern of ours when laying out the specification of how nodes would communicate was the case in which a node would have to communicate across a firewall.
+A concern when laying out the specification of how nodes would communicate was the case in which a node would have to communicate across a firewall.
 Firewalls add a great deal of complexity when designing a distributed system that is intended to be accessed by a large number of computers under diverse network constraints.
-Our ultimate decision was that since our project is academic in nature and limited in resources, we were going to ignore the cases in which communication over the allocated port is unavailable to a node.
-
+Since PBJ is currently academic in nature and limited in resources, we chose to ignore the cases in which communication over the allocated port is unavailable to a node.
+\section{Results}
 \subsection{Test Plan}
-In order to claim that we have designed a stable and scalable system with confidence, we needed to design a solid testing plan.
+In order to test that PBJ is a stable and scalable system, we needed to design a solid testing plan.
 In the design phase of our project, we thoroughly discussed the use of Condor, a HTC application that can deploy processes to a large number of computers, to test our network stability and search algorithms for large numbers of nodes.
@@
 Instead, we requested and were granted permission to perform our testing on Clemson's Palmetto cluster.
-Our account on the cluser utilized a shared network drive between nodes, so we had to write a script that would create a unique share file in a unique share directory.
-Each node was to have a single shared file for consistency.
-The end result was a test environment in which 300 search-able nodes with unique files were connected to our network.
+Our account on the cluster utilized a shared network drive between nodes, so we had to write a script that would create a unique share file in a unique share directory for every single node.
+Each node was to have a single shared file to keep search results to a minimum for testing purposes.
+The end result was a test environment in which 300 searchable nodes with unique files were connected to our network.
 
-We decided to focus our testing on the search performance and scalability of our network structure.
-To do this, we eliminated the sub networks so that every new node was designated as an ultra node.
-We also added additional functionality to the nodes to allow the gateway to tell a node to initiate a search.
-We designated ultra node 0 to be the searching node for our testing.
-The gateway was modified so that it initiated a search from node 0 upon the addition of a new node to the network.
-Node 0 then was to log the time the search took for each result, as well as how many hops the request made until each result was found.
-Nodes were added to the network at intervals of one second, which gave us 300 test results that describe the scalability of our system.
+We chose to focus our testing on search performance and the scalability of our network structure.
+To test this, we first eliminated the sub networks so that every new node was designated as an ultra node.
+We then added additional functionality to the nodes to allow the gateway to tell a node to initiate a search.
+We designated ultra node 0 to be the searching node for our testing cases.
+The gateway was modified so that it initiated a wildcard search from node 0 upon the addition of a new node to the network.
+Node 0 was to log the time the search took for each result, as well as how many hops the request made until each result was found.
+Nodes were added to the network at intervals of one second, which resulted in 300 discrete test results that describe the scalability of our system.
 
-%can we remove this paragraph? its pretty much fluff/no longer relevant
-%but i would feel bad deleting a whole paragraph without consulting
-The main goals of testing the gateway server was twofold.
-First, correct network topology was to be maintained when new nodes were added.
-This could easily be checked by feeding the gateway a large number of pseudo nodes to verify that the intended topology could be maintained for any size network.
-Furthermore, an applet was developed to display an image representing the network graph, making it easier to see node to node connections.
-The second goal of gateway testing was to verify that any dropped node notifications were being handled correctly, which involved updating the network structure for addition of future nodes.
-This is further discussed later when testing node functions.
+\subsection{Analysis}
 
-%our we going to talk about our other "testing" or just the palmetto stuff? if the latter, del this too
-Testing node functionality proved to be much more in depth.
-For this, we developed a series of repeatable test cases that the network should be able to handle.
-These test cases included: initiating a search as an ultra node, initiating a search as a node, searching from one end of the network to the other, searching from the middle of the network to either end, and downloading a search result.
-We also monitored the gateway to ensure that the network structure was maintained and rebuilt after all node disconnection scenarios: dropping a node from the beginning, middle, and end of the network, as well as dropping an ultra node from the beginning, middle, and end of the network.
-We repeated these test cases after every change we made to ensure that PBJ was stable and working properly.
-\section{Analysis}
-
-Our testing demonstrated to us the stability of the network.
+Our testing demonstrated to us the stability[a] of the network.
 To a large extent, the main goals of the project were met.
-A network of connected peers could be created using only a simple centralized gateway, while keeping file searching and downloading independent of such a server.
-We discovered, however, that there was a large amount of traffic on the network between the pinging of peers and redundant searching, even reduced as it is with the unique request ID.
+A network of connected peers could be created using only a slightly centralized bootstrapping process, while keeping file searching and downloading completely decentralized.
+We discovered that there was a large amount of traffic on the network between the pinging of peers and redundant searching, even reduced as it is with the unique request ID.
 We also feel that an explicit ttl will eventually limit PBJ’s scalability.
@@
 Many of the spikes in search time are likely due to network latency.
-When ultra node 0 reaches its next connection with ultra node 256, both the average and total search time become much less volitile, likely due to the fact that far fewer hops are now required to reach the highest ultra peers.
+When ultra node 0 reaches its next connection with ultra node 256, both the average and total search time become much less volatile, likely due to the fact that far fewer hops are now required to reach the highest ultra peers.
 These numbers represent an idle network where the only messages being passed are search requests from ultra node 0.
@@
 
-The data for the maximum number of hops to traverse the network seems to imply that a pre defined ttl would quickly limit the ability of the network to find files in the system.
+The data for the maximum number of hops to traverse the network seems to imply that a pre-defined ttl would quickly limit the ability of the network to find files in the system.
 Initially, the maximum number of hops is very unstable, with large changes between a few ultra peers.
@@
 \subsubsection{Decentralization}
-One improvement previously discussed is changing how nodes join the system.
+One improvement previously discussed is decentralizing the bootstrapping process.
 The current gateway method functions well, but its centralized nature is hardly ideal for a system whose design so highlights decentralization.
@@
 
-PBJ is a decentralized file sharing system whose highly connected nodes, search algorithm, and intelligent node loss handling make the ground work for a stable and reliable application.
-PBJ is heavily influenced by existing file sharing services gnutella and to a much lesser extent Napster.
+PBJ is a decentralized file sharing system whose highly connected nodes, search algorithm, and intelligent node loss handling form the ground work for a stable and reliable P2P application.
+PBJ is heavily influenced by existing file sharing services such as gnutella and to a much lesser extent Napster.
+
 PBJ users connect to the system through a dedicated gateway, either becoming ultra nodes connected to other ultra nodes or part of an ultra node’s sub network.
 Searching the network is done by keyword comparison to filenames, and search requests are broadcast between ultra peers.
+Results are reported to the searching node, which then has the option of downloading the file from any of the responding nodes.
 
- Results are displayed to the user to choose a result to download.
-The gateway and the nodes themselves periodically ping their connections.
+To ensure the refilling of holes in the network, the gateway and the nodes themselves periodically ping their connections.
 If an ultra peer does not respond to a ping, it is removed from the ultra node’s active connections.
 If a sub network node’s ultra node does not respond, the node will exit the network and attempt to reconnect through the gateway.
-Every time the gateway attempts add a node, it first checks that existing ultra peers are connected.
-If one has gone down, the node to be added is added in that ultra peer’s place.
-PBJ uses Flask for network communication.
+Every time the gateway attempts add a node, it first checks that all of the existing ultra nodes are online.
+If one has lost connectivity, the new node to be added is added in that ultra node’s place.
+
+We tested the scalability of our network using Clemson Unversity’s Palmetto cluster, which allowed us to fill our network with 300 ultra nodes.
+To test the scalability of our network, we ran an automated test that measured the speed and distance traveled by a search request as the network grew in size.
+What we found is that even with 300 ultra nodes, the maximum number of hops that a search request took was 8.
+Because there is no limit to the number of nodes in an ultra node’s sub network, our network can propagate a request to an extremely large number of nodes with a minimal number of hops.
 
@@
 The authors would like to thank Dr.
-Goasguen for his help and advice, the Clemson University Systems staff for quickly responding to the various technical problems and hurdles faced in setting up machines for testing, and Dunkin Donuts for making their delicious coffee the authors used in the majority of this project.
+Goasguen for his help and advice, the Clemson University Systems staff for quickly responding to the various technical problems and hurdles faced in setting up machines for testing, and Dunkin’ Donuts for making their delicious coffee the authors used in the majority of this project.
 

### 2012-01-11 paper/paper.tex
paper

@@
 
-% for over three affiliations, or if they all won't fit within the width
+% for over three affiliations, or if they all won`t fit within the width
 % of the page, use this alternative format:
@@
 % if the conference you are submitting to favors bold math in the abstract,
-% then you can use LaTeX's standard command \boldmath at the very start
+% then you can use LaTeX`s standard command \boldmath at the very start
 % of the abstract to achieve this. Many IEEE journals/conferences frown on
@@
 The ability to search for and download music free of charge was very popular and the Napster user base grew very large in the late 1990s and early 2000s.
-It also happened that a large percentage of the downloads on Napster constituted copyright infringement, since users were distributing copyrighted music without the creator’s consent.
-From a legal standpoint, the flaw in Napster’s design was that all of the files on the system were indexed on the central server, including files that broke copyright.
+It also happened that a large percentage of the downloads on Napster constituted copyright infringement, since users were distributing copyrighted music without the creator`s consent.
+From a legal standpoint, the flaw in Napster`s design was that all of the files on the system were indexed on the central server, including files that broke copyright.
 This meant that legally, Napster knew about and facilitated copyright infringement.
@@
 Because Napster was a centralized application, the network ceased to exist when the server was taken down.
-File sharing applications developed after Napster’s shut down attempted to avoid legal liability by making their applications less centralized and by not having any centralized elements keep track of individual files.
+File sharing applications developed after Napster`s shut down attempted to avoid legal liability by making their applications less centralized and by not having any centralized elements keep track of individual files.
 Napster exists today as a subscription based service ~\cite{napster}
@@
 Gnutella (a portmanteau of GNU, the free software project, and Nutella, the chocolate and hazelnut spread) is a decentralized network of interconnected users running a gnutella client called a node.
-Search requests are broadcast to all of the searching node’s neighbor clients (which gnutella terms ‘peers’), which in turn broadcast the request to all of their peers as well ~\cite{lookup}.
+Search requests are broadcast to all of the searching node`s neighbor clients (which gnutella terms `peers`), which in turn broadcast the request to all of their peers as well ~\cite{lookup}.
 Look-up in gnutella is $O(log n)$ where $n$ is the number of peers in the system.~\cite{super peer} This goes on until the file is found or the request goes a specified number of peer hops without finding a file (much like the time to live field in an IP packet).
@@
 This hop based searching algorithm does allow for the possibility that a search request may fail to return a file in the network, especially as the network gets larger and larger.
-Later versions of gnutella’s network introduced the concept of ultra nodes and ultra peers ~\cite{evo}.
+Later versions of gnutella`s network introduced the concept of ultra nodes and ultra peers ~\cite{evo}.
 Each ultra node is connected to a network of regular nodes as well as a large number of other ultra nodes, each having its own network of nodes, making gnutella a network of networks.
@@
  Like gnutella, PBJ contains a network of ultra nodes.
-Each of these ultra nodes has a set of nodes that form an ultra node’s sub network.
+Each of these ultra nodes has a set of nodes that form an ultra node`s sub network.
 Ultra nodes in PBJ are given a unique ID starting at 0 and increasing by one each time a new ultra node is added to the network.
-An ultra node's ID is assigned in the gateway when it is added to the network.
+An ultra node`s ID is assigned in the gateway when it is added to the network.
 This unique ID is a vital element to building the network.
@@
 These decisions by the gateway essentially dictate how the network is built.
-We devised two separate algorithms for building the network; the one we actually implemented is described here and the other is detailed in the section ‘Future Work’.
+We devised two separate algorithms for building the network; the one we actually implemented is described here and the other is detailed in the section `Future Work`.
 As implemented, the first node to enter the network becomes ultra node 0.
-If, for example, there are three nodes per ultra node, the next three nodes to connect would become node 0’s sub network.
+If, for example, there are three nodes per ultra node, the next three nodes to connect would become node 0`s sub network.
 The fifth node to join the network would become ultra node 1 and would connect to ultra node 0.
-In this scheme of building the network, each ultra node’s sub network is filled before the next ultra node is created.
+In this scheme of building the network, each ultra node`s sub network is filled before the next ultra node is created.
 This algorithm ensures that the graph has the smallest number of ultra nodes possible in a system and all but potentially the last ultra node have filled sub networks.
@@
 The PBJ client allows a share path to be passed as a command line argument.
-The default share directory is a sub-directory named ‘share’.
-All files and sub directories in the userÕs share directory will be available to the network for other nodes to download.
+The default share directory is a sub-directory named `share`.
+All files and sub directories in the userÍs share directory will be available to the network for other nodes to download.
 When a user wants to search, they enter a keyword and submit a search request.
-The search request will be sent to the searching nodeÕs ultra node (unless the node is itself an ultra node).
+The search request will be sent to the searching nodeÍs ultra node (unless the node is itself an ultra node).
 \begin{figure}[tbh]
@@
  The ultra node will send the search request to all of the other peers in its sub network before broadcasting it to its connected ultra peers.
-Search requests consist of four major parts - the searching node’s address, the keyword, a search id, and the time to live (ttl).
+Search requests consist of four major parts - the searching node`s address, the keyword, a search id, and the time to live (ttl).
 The ttl is initially set to a positive integer.
@@
 The instance of the Flask server is told to use on a random port that is not currently in use.
-Flask was not available as an installed Python module on the machines that we used testing, and we lacked administrative privileges to install it.
+Flask was not available as an installed Python module on the machines that we used during testing, and we lacked administrative privileges to install it.
 To install and use Flask on every lab machine without modifying any system files, PBJ uses virtualenv ~\cite{virtual}, which is a tool used to create virtual Python environments.
@@
 In the design phase of our project, we thoroughly discussed the use of Condor, a HTC application that can deploy processes to a large number of computers, to test our network stability and search algorithms for large numbers of nodes.
-Unfortunately, the computers on Clemson’s Condor network are equipped with Windows Firewall, which blocks the access of ports that have not been explicitly granted permission.
+Unfortunately, the computers on Clemson`s Condor network are equipped with Windows Firewall, which blocks the access of ports that have not been explicitly granted permission.
 As previously discussed, we will be ignoring the cases in which our nodes are behind firewalls, so this test strategy was inadequate.
-Instead, we requested and were granted permission to perform our testing on Clemson's Palmetto cluster.
+Instead, we requested and were granted permission to perform our testing on Clemson`s Palmetto cluster.
 Our account on the cluster utilized a shared network drive between nodes, so we had to write a script that would create a unique share file in a unique share directory for every single node.
@@
 
-Our testing demonstrated to us the stability[a] of the network.
+Our testing demonstrated to us the stability of the network.
 To a large extent, the main goals of the project were met.
@@
 We discovered that there was a large amount of traffic on the network between the pinging of peers and redundant searching, even reduced as it is with the unique request ID.
-We also feel that an explicit ttl will eventually limit PBJ’s scalability.
+We also feel that an explicit ttl will eventually limit PBJ`s scalability.
 This section provides an in depth look at our test results and possible improvements future versions of our system could implement to deal with these perceived issues.
@@
 
-Our results show that there is a high correlation between network structure and the number of hops required to reach all the nodes on the system.
+Our results also show that there is a high correlation between network structure and the number of hops required to reach all the nodes on the system.
 Looking at the average number of hops to reach every ultra peer in a network, several trends become apparent.
-First, every time an ultra peer with an even power of two connects to ultra peer 0, (ultra peers 4, 16, 64, and 256) the average number of hops to traverse the network decreases by approximately one hop.
+First, every time an ultra peer with an even power of two connects to ultra peer 0, (ultra peers 4, 16, 64, and 256) the average number of hops to traverse the network decreases, usually by approximately half a hop.
+This drop occurs because ultra node 0 now has an additional connection through which it can reach other nodes.
+Also, this new connection will facilitate sending requests to nodes that were previously farthest away from node 0.
+This explains why the drop in  the average number of hops is so large when a new connection is added.
 Once this drop has occurred, as new ultra peers are added to the network, the average number of hops grows at a roughly linear rate to about one more hop on average than the previous peak.
-Notice that the slope between peaks is decreasing with an increasing number of nodes.
+Notice that the slope of a trend line drawn between a trough and next peak decreases with an increasing number of nodes.
 This implies that as PBJ gets more and more ultra peers, the addition of ultra peers will have less of an impact on average number of hops to find a file.
+As the network grows, so does the level of redundancy in the network.
+More potential pathways between two ultra peers are created and the loss of ultra peers will have less of an effect on the functionality of the whole system.
+Since PBJ replaces holes in the network of ultra peers before expanding the network, PBJ is relatively successful at ensuring that redundancy is not lost with the constant logging in and out of users.
 
@@
 Several different specific algorithms for how exactly the network is organized were discussed.
-The current algorithm, described above, creates a new ultra node and then fills that ultra node’s sub network before creating a new ultra peer.
-While this algorithm works acceptably, it ignores several observations about PBJ’s network.
+The current algorithm, described above, creates a new ultra node and then fills that ultra node`s sub network before creating a new ultra peer.
+While this algorithm works acceptably, it ignores several observations about PBJ`s network.
 In PBJ, the number of hops it takes to get from node A to node B is highly dependent on the current number of ultra peers in the system.
@@
 When creating a new network, the first eight (eight is half of sixteen) nodes into the system will become the first eight ultra peers.
-The next nodes to join the system will join these ultra peers’ sub networks.
+The next nodes to join the system will join these ultra peers` sub networks.
 When all eight sub networks have been filled, the gateway then add the next nodes as ultra peers in the system until there are thirty-two ultra peers (thirty two is half of sixty four) in the system.
@@
 
-PBJ users connect to the system through a dedicated gateway, either becoming ultra nodes connected to other ultra nodes or part of an ultra node’s sub network.
+PBJ users connect to the system through a dedicated gateway, either becoming ultra nodes connected to other ultra nodes or part of an ultra node`s sub network.
 Searching the network is done by keyword comparison to filenames, and search requests are broadcast between ultra peers.
@@
 To ensure the refilling of holes in the network, the gateway and the nodes themselves periodically ping their connections.
-If an ultra peer does not respond to a ping, it is removed from the ultra node’s active connections.
-If a sub network node’s ultra node does not respond, the node will exit the network and attempt to reconnect through the gateway.
+If an ultra peer does not respond to a ping, it is removed from the ultra node`s active connections.
+If a sub network node`s ultra node does not respond, the node will exit the network and attempt to reconnect through the gateway.
 Every time the gateway attempts add a node, it first checks that all of the existing ultra nodes are online.
-If one has lost connectivity, the new node to be added is added in that ultra node’s place.
+If one has lost connectivity, the new node to be added is added in that ultra node`s place.
 
-We tested the scalability of our network using Clemson Unversity’s Palmetto cluster, which allowed us to fill our network with 300 ultra nodes.
+We tested the scalability of our network using Clemson Unversity`s Palmetto cluster, which allowed us to fill our network with 300 ultra nodes.
 To test the scalability of our network, we ran an automated test that measured the speed and distance traveled by a search request as the network grew in size.
 What we found is that even with 300 ultra nodes, the maximum number of hops that a search request took was 8.
-Because there is no limit to the number of nodes in an ultra node’s sub network, our network can propagate a request to an extremely large number of nodes with a minimal number of hops.
+Because there is no limit to the number of nodes in an ultra node`s sub network, our network can propagate a request to an extremely large number of nodes with a minimal number of hops.
 
@@
 Based on this testing, however, we have a number of future improvements to PBJ.
-These improvements would increase the network’s stability, decrease redundant traffic, and reach a larger percentage of the network.
+These improvements would increase the network`s stability, decrease redundant traffic, and reach a larger percentage of the network.
 
@@
 The authors would like to thank Dr.
-Goasguen for his help and advice, the Clemson University Systems staff for quickly responding to the various technical problems and hurdles faced in setting up machines for testing, and Dunkin’ Donuts for making their delicious coffee the authors used in the majority of this project.
+Goasguen for his help and advice, the Clemson University Systems staff for quickly responding to the various technical problems and hurdles faced in setting up machines for testing, and Dunkin` Donuts for making their delicious coffee the authors used in the majority of this project.
 
@@
 
-% that's all folks
+% that`s all folks
 \end{document}

### 2012-01-17 paper/paper.tex
paper

@@
 \boldmath
-A common basis of differentiating peer to peer (P2P) file sharing applications is by their degree of centralization, or how reliant the application is on a single central element.
-Some applications, like Napster, rely completely on a central server for organizing users and searching for files.
-This kind of structure simplifies system organization and ensures constant time searching.
-It also places the burden of the entire system on the server and server failure leads to a total loss of functionality.
-Other applications, like gnutella, have no central node, instead connecting users together and passing search requests between users.
-This removes the chance of system failure from loss of a single entity, but complicates the network and makes searching less efficient.
-The design decisions apparent in these applications affect virtually every aspect of their functionality and stability.
-
-PBJ (Please Be Jenerous) is a file sharing application designed to marry the positive aspects of the centralized and decentralized paradigms.
+In this paper we present PBJ (Please Be Jenerous), a file sharing application designed to marry the positive aspects of the centralized and decentralized paradigms.
 PBJ users are connected to each other to form a network of users, and requests are passed among them.
@@
 The PBJ gateway allows for increased network stability and efficiency, and if the gateway should go down, existing users can function without it.
+Our results show that a PBJ network with 300 ultra nodes can locate a file in the network in four hops on average.
 
@@
 \section{Introduction}
+\begin{comment}{
+
+A common basis of differentiating peer to peer (P2P) file sharing applications is by their degree of centralization, or how reliant the application is on a single central element.
+Some applications, like Napster, rely completely on a central server for organizing users and searching for files.
+This kind of structure simplifies system organization and ensures constant time searching.
+It also places the burden of the entire system on the server and server failure leads to a total loss of functionality.
+Other applications, like gnutella, have no central node, instead connecting users together and passing search requests between users.
+This removes the chance of system failure from loss of a single entity, but complicates the network and makes searching less efficient.
+The design decisions apparent in these applications affect virtually every aspect of their functionality and stability.
+\end{comment}
 
@@
 
+ The novel something something of PBJ are something something
+
+ This paper is organized as follows : blah blah blah.
+
 \section{Related Work}
-\subsection{Napster}
 A defining characteristic of a P2P file sharing application is the kind of network topology it employs.
-Napster, one of the first file sharing networks, was a highly centralized system.
+Napster REFERENCE HERE, one of the first file sharing networks, was a highly centralized system.
 All Napster users connected to a central server.
-Each user would have a folder designated for sharing audio files (only mp3s were transferred on Napster).
+Each user would have a folder designated for sharing audio files.
 This central server would handle a user request by searching for related files in the share folders of other users.
@@
 
-The ability to search for and download music free of charge was very popular and the Napster user base grew very large in the late 1990s and early 2000s.
-It also happened that a large percentage of the downloads on Napster constituted copyright infringement, since users were distributing copyrighted music without the creator`s consent.
-From a legal standpoint, the flaw in Napster`s design was that all of the files on the system were indexed on the central server, including files that broke copyright.
-This meant that legally, Napster knew about and facilitated copyright infringement.
-In 2001, when the inevitable flood of lawsuits were filed against Napster, a court order shut down the central server.
+In 2001, Napster was ordered to shut down their central server due to copyright infringement.
 Because Napster was a centralized application, the network ceased to exist when the server was taken down.
@@
 Napster exists today as a subscription based service ~\cite{napster}
-\begin{comment}
-  \subsection{BitTorrent}
- With the dismantling of Napster, file sharing applications started to become more complex and decentralized.
-Most file sharing today involves the BitTorrent protocol ~\cite{bit}.
-BitTorrent differs from other file sharing systems in that it downloads file segments from multiple sources instead of a single file transfer between two users.
-BitTorrent works by having a user obtain a torrent file (usually by downloading it from a website).
-The local BitTorrent client interprets the contents of the torrent file and connects with a tracker, a server with information about how to find the file.
- The tracker finds seeders, other BitTorrent clients, with a local copy of the file to be transferred.
-The file also identifies the swarm, a set of clients with a portion of the file, usually in the process of downloading it themselves.
-The searching client downloads from these sources simultaneously to build the desired file.
-BitTorrent is especially useful for downloading popular files, since there will be a large pool of seeders and a large swarm.
-While BitTorrent is clearly more distributed than Napster, since there are multiple central servers instead of a single large server for the entire application.
-However, if the tracker(s) in a torrent file are taken down, there is no way that torrent file can be used to obtain the actual file.
- \end{comment}
 
-   \subsection{Gnutella}
-Gnutella (a portmanteau of GNU, the free software project, and Nutella, the chocolate and hazelnut spread) is a decentralized network of interconnected users running a gnutella client called a node.
+Gnutella is a decentralized network of interconnected users running a gnutella client called a node.
 Search requests are broadcast to all of the searching node`s neighbor clients (which gnutella terms `peers`), which in turn broadcast the request to all of their peers as well ~\cite{lookup}.
-Look-up in gnutella is $O(log n)$ where $n$ is the number of peers in the system.~\cite{super peer} This goes on until the file is found or the request goes a specified number of peer hops without finding a file (much like the time to live field in an IP packet).
-A list of the files that match the search are displayed to the user, who then chooses the file to download.
-The searching node connects directly to the node with the desired file for file transfer.
-This hop based searching algorithm does allow for the possibility that a search request may fail to return a file in the network, especially as the network gets larger and larger.
-Later versions of gnutella`s network introduced the concept of ultra nodes and ultra peers ~\cite{evo}.
+Look-up in gnutella is $O(log n)$ where $n$ is the number of peers in the system.~\cite{superpeer} If a file is not found in a specified number hops (much like the time to live field in an IP packet) the search ends.
+When a desired file has been found, the searching node connects directly to the node with the desired file for transfer.
+This hop based searching algorithm does allow for the possibility that a search request may fail to return a file in the network as the network grows.
+Later versions of gnutella introduced the concept of ultra nodes and ultra peers ~\cite{evo}.
 Each ultra node is connected to a network of regular nodes as well as a large number of other ultra nodes, each having its own network of nodes, making gnutella a network of networks.
-The reason for this change is that it allows many more nodes to be reached from any one node in a smaller number of hops, making searching more efficient and the system more scalable.
-Nodes keep track of the other nodes they have previously connected with and attempt to reconnect to the network through these nodes.
+This change makes searching more efficient and the system more scalable since many more nodes can be reached in a smaller number of hops.
+Nodes keep track of nodes they have previously connected with and attempt to reconnect to the network through these nodes.
 When connecting for the first time, these nodes must attempt to connect a set of nodes guaranteed to be in the gnutella network.
@@
 \end{figure}
-The basic algorithm for connecting ultra nodes in the network can be visualized as an outward spiral of ultra peers.
+The basic algorithm for connecting ultra nodes in the network can be visualized as an outward spiral of ultra peers, as shown in Figure 1.
 While this alone would be wildly inefficient in terms of searching and stability, new ultra nodes also connect to ultra nodes deeper within the spiral.
@@
 These decisions by the gateway essentially dictate how the network is built.
-We devised two separate algorithms for building the network; the one we actually implemented is described here and the other is detailed in the section `Future Work`.
 As implemented, the first node to enter the network becomes ultra node 0.
@@
 
-The PBJ client allows a share path to be passed as a command line argument.
+The PBJ client allows a shared path to be passed as a command line argument.
 The default share directory is a sub-directory named `share`.
-All files and sub directories in the userÍs share directory will be available to the network for other nodes to download.
+All files and sub directories in the user`s share directory will be available to the network for other nodes to download.
 When a user wants to search, they enter a keyword and submit a search request.
-The search request will be sent to the searching nodeÍs ultra node (unless the node is itself an ultra node).
+The search request will be sent to the searching node`s ultra node (unless the node is itself an ultra node).
 \begin{figure}[tbh]
@@
 This scheme vastly cuts down the amount of redundant request traffic and makes the system more efficient as a whole.
+
 \subsection{Disconnecting from the Network}
@@
 \section{Implementation}
-All of the PBJ network communication is facilitated through the use of the Flask python module.
+PBJ was written and implemented using Python version 2.7. The code written specifically for PBJ totals approximately 1500 lines.
+All of the PBJ network communication is facilitated through the use of the Flask python framework.
 Flask ~\cite{flask} is a web micro-framework that is designed to simplify the development of Python web applications.
@@
 Every node, as well as the gateway, is running an instance of a Flask server.
-The instance of the Flask server is told to use on a random port that is not currently in use.
-Flask was not available as an installed Python module on the machines that we used during testing, and we lacked administrative privileges to install it.
-To install and use Flask on every lab machine without modifying any system files, PBJ uses virtualenv ~\cite{virtual}, which is a tool used to create virtual Python environments.
+The instance of the Flask server is told to use a random port that is not currently in use.
+To install and use Flask a machine without modifying any system files, PBJ uses virtualenv ~\cite{virtual}, which is a tool used to create virtual Python environments.
 A virtual Python environment can be created in a users home folder on a system using virtualenv, and then that user has permission to modify that environment however they wish.
@@
 Since PBJ is currently academic in nature and limited in resources, we chose to ignore the cases in which communication over the allocated port is unavailable to a node.
+
 \section{Results}
@@
 In order to test that PBJ is a stable and scalable system, we needed to design a solid testing plan.
-In the design phase of our project, we thoroughly discussed the use of Condor, a HTC application that can deploy processes to a large number of computers, to test our network stability and search algorithms for large numbers of nodes.
+In the design phase of our project, we thoroughly discussed the use of Condor ~\cite{condor}, a HTC application that can deploy processes to a large number of computers, to test our network stability and search algorithms for large numbers of nodes.
 Unfortunately, the computers on Clemson`s Condor network are equipped with Windows Firewall, which blocks the access of ports that have not been explicitly granted permission.
-As previously discussed, we will be ignoring the cases in which our nodes are behind firewalls, so this test strategy was inadequate.
-Instead, we requested and were granted permission to perform our testing on Clemson`s Palmetto cluster.
+Instead, performed our testing on Clemson`s Palmetto cluster, a 12,000 core Linux cluster ~\cite{palmetto}.
 Our account on the cluster utilized a shared network drive between nodes, so we had to write a script that would create a unique share file in a unique share directory for every single node.
@@
 The end result was a test environment in which 300 searchable nodes with unique files were connected to our network.
+As our results demonstrate, the performance of PBJ depends on the total number of ultra nodes in the system.
+Performance is dramatically affected when the total number of ultra nodes reaches an even power of 2.
+We were unable to obtain more than 1024 cores from Palmetto, we chose 300 cores because it was sufficiently above 256.
 
@@
 
-Our testing demonstrated to us the stability of the network.
-To a large extent, the main goals of the project were met.
-A network of connected peers could be created using only a slightly centralized bootstrapping process, while keeping file searching and downloading completely decentralized.
-We discovered that there was a large amount of traffic on the network between the pinging of peers and redundant searching, even reduced as it is with the unique request ID.
-We also feel that an explicit ttl will eventually limit PBJ`s scalability.
-This section provides an in depth look at our test results and possible improvements future versions of our system could implement to deal with these perceived issues.
-
+Figure 3 shows the search time results show a positive linear trend with some obvious noise distortion.
+Many of the spikes in search time are likely due to network latency.
+When ultra node 0 reaches its next connection with ultra node 256, both the average and total search time become much less volatile, likely due to the fact that far fewer hops are now required to reach the highest ultra peers.
+These numbers represent an idle network where the only messages being passed are search requests from ultra node 0.
 \begin{figure}[tbh]
@@
 
-The search time results show a positive linear trend with some obvious noise distortion.
-Many of the spikes in search time are likely due to network latency.
-When ultra node 0 reaches its next connection with ultra node 256, both the average and total search time become much less volatile, likely due to the fact that far fewer hops are now required to reach the highest ultra peers.
-These numbers represent an idle network where the only messages being passed are search requests from ultra node 0.
 In actual use, there would be many messages concurrently, so it is likely that search times would be higher than shown here.
@@
 
-Our results also show that there is a high correlation between network structure and the number of hops required to reach all the nodes on the system.
+Figure 4 demonstrates a high correlation between network structure and the number of hops required to reach all the nodes on the system.
 Looking at the average number of hops to reach every ultra peer in a network, several trends become apparent.
@@
 
-\subsection{Future Work}
+Our testing demonstrated to us the stability of the network.
+To a large extent, the main goals of the project were met.
+A network of connected peers could be created using only a slightly centralized bootstrapping process, while keeping file searching and downloading completely decentralized.
+We discovered that there was a large amount of traffic on the network between the pinging of peers and redundant searching, even reduced as it is with the unique request ID.
+We also feel that an explicit ttl will eventually limit PBJ`s scalability.
+This section provides an in depth look at our test results and possible improvements future versions of our system could implement to deal with these perceived issues.
 
-\subsubsection{Decentralization}
-One improvement previously discussed is decentralizing the bootstrapping process.
-The current gateway method functions well, but its centralized nature is hardly ideal for a system whose design so highlights decentralization.
-Several alternatives have been discussed.
-The most likely implementation would be to place the burden of network building on the existing ultra nodes.
-A node would keep track of its previously connected ultra nodes and attempt to connect to these peers.
-Depending on its current status, the ultra peer might add the new users or decide to push it towards higher valued ultra peers to attempt placement.
-Eventually it would either get placed in a sub network or reach the ultra peer with the highest id and become the new highest ultra peer.
-If none of the previously connected nodes are currently connected to the network, a range of options could be implemented to ensure the user gets into the network including but not limited to: keeping the gateway as a backup, having ultra nodes at known URLs, placing the burden on the user to find the information.
+\section{Future Work and Conclusion}
 
-\subsubsection{Network topology}
-Several different specific algorithms for how exactly the network is organized were discussed.
-The current algorithm, described above, creates a new ultra node and then fills that ultra node`s sub network before creating a new ultra peer.
-While this algorithm works acceptably, it ignores several observations about PBJ`s network.
-In PBJ, the number of hops it takes to get from node A to node B is highly dependent on the current number of ultra peers in the system.
-As a simple example, the optimal number of hops from ultra peers 0 to 63 is 5 hops (0-16-32-48-47-63) if ultra node 64 does not exist and 2 hops (0 -64-63) if ultra node 64 does exist.
-Indeed, a node whose largest hop was one of the last nodes to be added has the optimal network structure for searching.
-
- Our algorithm for taking advantage of this trait slightly alters how the network is built by the gateway.
-The basic idea behind this algorithm is to have an ultra peer back bone in place first with empty sub networks and then fill in the sub networks.
-When creating a new network, the first eight (eight is half of sixteen) nodes into the system will become the first eight ultra peers.
-The next nodes to join the system will join these ultra peers` sub networks.
-When all eight sub networks have been filled, the gateway then add the next nodes as ultra peers in the system until there are thirty-two ultra peers (thirty two is half of sixty four) in the system.
-This continues so that when the network is full, it grows to half the size of the next even power of two before filling in the ultra peers.
-This ensures that the majority of the peers are close together but have the ability to move farther because there is an ultra peer structure in place to facilitate such movement.
+In the future, we would like to pursue several possible improvements to PBJ.
+One improvement which has been discussed is decentralizing the bootstrapping process by decentralizing the gateway.
+As our results show, the networkÕs performance improves once the total number of ultra nodes reaches an even power of 2.
+An algorithm that takes advantage of this trait would slightly alter how the network is built by the gateway.
+The basic idea would be to create an ultra peer back bone with empty sub networks and then fill in the sub networks.
 Another potential improvement would be to choose ultra peers based on network quality.
@@
 This would help stabilize the network and improve quality.
-
-\subsubsection{Searching}
-We also feel the search algorithm could be improved or a new algorithm implemented.
-Going forward, it seems that the ttl is the main issue to be addressed.
-Its purpose is to limit system traffic, but if the network becomes large enough, it is possible searches from a certain node will never reach other machines far enough away in the network.
-Though additional testing would be necessary, we would need to see the effects of larger ttl values on system traffic.
-It may make sense to remove the ttl all together and count on the unique ID checking to limit redundant network traffic.
-We have also discussed tiers of ttl values corresponding to the size of the hop to be taken.
-This algorithm is still early in development and would need more research.
-
-\subsubsection{Stabilization}
-Handling node failure was a tough challenge in early development.
-As convenient and stabilizing as our node ping method for detecting disconnected nodes is to the network, it leads to a lot of network traffic.
-Currently, nodes ping each other every few seconds.
-It might make sense to have nodes ping only right before sending a search request, or to implement some kind of TCP style application level three way hand shake.
-In addition, it might make sense for ultra nodes to contact the gateway when they have lost contact with an ultra peer, rather than having the gateway ping all ultra nodes in the network.
-
-\subsubsection{User experience}
+Improvements could also be made to PBJÕs search algorithm, specifically its handling of search ttl.
+It may make sense to have a ttl that scales with the size of the network, or to remove ttl altogether from searching.
 Simple things such as an improved GUI and security/privacy features could also be added to make the system more user friendly.
 Another concern we have is attempting to mitigate is leeching, the practice where by users of a file sharing network do not share any files to be downloaded but still use the network to get files.
-
-\section{Conclusion}
 
@@
 % use section* for acknowledgement
-\section*{Acknowledgment}
-
-The authors would like to thank Dr.
-Goasguen for his help and advice, the Clemson University Systems staff for quickly responding to the various technical problems and hurdles faced in setting up machines for testing, and Dunkin` Donuts for making their delicious coffee the authors used in the majority of this project.
 
@@
 Matei Ripeanu, Adriana Iamnitchi, Ian Foster. "Mapping the Gnutella Network". \emph{IEEE Internet Computing}, January-February 2002.  
+\bibitem{condor}
+Condor Website : http://research.cs.wisc.edu/condor/
+\bibitem{palmetto}
+Palmetto Cluster Website : citi.clemson.edu/palmetto
 

### 2012-01-18 paper/paper.tex
a

@@
 \maketitle
-
 \begin{abstract}
 \boldmath
-In this paper we present PBJ (Please Be Jenerous), a file sharing application designed to marry the positive aspects of the centralized and decentralized paradigms.
+In this paper we present PBJ (Please Be Jenerous), a novel file sharing application designed to marry the positive aspects of the centralized and decentralized paradigms.
 PBJ users are connected to each other to form a network of users, and requests are passed among them.
-To connect users to the system, PBJ uses a central gateway as a simple, powerful way to control the way the network is built to optimize the network.
+To connect users to the system, PBJ uses a central gateway as a simple, yet powerful way to control and optimize the way the network is built.
 The PBJ gateway allows for increased network stability and efficiency, and if the gateway should go down, existing users can function without it.
 Our results show that a PBJ network with 300 ultra nodes can locate a file in the network in four hops on average.
+Average search time for a file in PBJ network of 300 nodes is 0.75 sec.
 
@@
 This kind of structure simplifies system organization and ensures constant time searching.
-It also places the burden of the entire system on the server and server failure leads to a total loss of functionality.
+However, it places the burden of the entire system on the server.
+Therefore, server failure leads to a total loss of functionality.
 Other applications, like gnutella, have no central node, instead connecting users together and passing search requests between users.
@@
 
- The novel something something of PBJ are something something
+ The novelty of PBJ lies within its connectivity. something something devised highly connected ultranode graph somethnig something redundancy something hops
 
- This paper is organized as follows : blah blah blah.
+ This paper is organized as follows : Section 2 discusses existing file sharing systems.
+Section 3 describes several of the algorithms PBJ uses.
+In section 4, the implementation details of PBJ are explained.
+A layout of our test plan and the associated results can be found in section 5.
+Future work and our conclusions are contained in section 6.
 
@@
 A defining characteristic of a P2P file sharing application is the kind of network topology it employs.
-Napster REFERENCE HERE, one of the first file sharing networks, was a highly centralized system.
+Napster ~\cite{nap}, one of the first file sharing networks, was a highly centralized system.
 All Napster users connected to a central server.
@@
 
-Gnutella is a decentralized network of interconnected users running a gnutella client called a node.
+Gnutella ~\cite{gnut} is a decentralized network of interconnected users running a gnutella client called a node.
 Search requests are broadcast to all of the searching node`s neighbor clients (which gnutella terms `peers`), which in turn broadcast the request to all of their peers as well ~\cite{lookup}.
@@
 
-\section{Methodology}
 PBJ takes key design qualities of gnutella and uses them only as a starting point, rather than implementing a version of the actual gnutella protocol.
@@
 
+\section{Methodology}
 \subsection{Building the Network}
@@
 \end{figure}
+For PBJ, a novel algorithm for building the network was conceived that attempts to keep all of the nodes in a network within a few hops of each other.
 The basic algorithm for connecting ultra nodes in the network can be visualized as an outward spiral of ultra peers, as shown in Figure 1.
@@
 Performance is dramatically affected when the total number of ultra nodes reaches an even power of 2.
-We were unable to obtain more than 1024 cores from Palmetto, we chose 300 cores because it was sufficiently above 256.
+We were unable to obtain more than 1024 nodes from Palmetto.
+This lead us to choose 300 test nodes because it was sufficiently above 256.
 
@@
 We also feel that an explicit ttl will eventually limit PBJ`s scalability.
-This section provides an in depth look at our test results and possible improvements future versions of our system could implement to deal with these perceived issues.
+Based on this testing, we have a number of future improvements to PBJ.
+These improvements would increase the network`s stability, decrease redundant traffic, and reach a larger percentage of the network.
 
@@
 Because there is no limit to the number of nodes in an ultra node`s sub network, our network can propagate a request to an extremely large number of nodes with a minimal number of hops.
-
-Thorough unit testing of both gateway server and node application functions proved the functionality of the PBJ network.
-It also let us see what areas of the sharing system need the most attention in order to improve performance.
-Network scalability and stability were seen to be correct and fully functional as intended.
-Based on this testing, however, we have a number of future improvements to PBJ.
-These improvements would increase the network`s stability, decrease redundant traffic, and reach a larger percentage of the network.
 
@@
 Hendrik Schuleze and Klaus Mochalski. "Internet Study 2008/2009". Ipoque Leipzig Germany, 2009
+\bibitem{nap}
+Original Napster Specification : http://opennap.sourceforge.net/napster.txt
 \bibitem{superpeer}
 Alper Tugay Misrak et al. "Structured Superpeers: Leveraging Heterogeneity to Provide Constant-Time Lookup" . \emph{WIAPP 2003 Proceedings}
+\bibitem{gnut}
+Gnutella Website : rfc-gnutella.sourceforge.net
 \bibitem{saroiu}

### 2012-01-18 paper/paper.tex
paper

@@
 \section{Introduction}
-\begin{comment}{
-
-A common basis of differentiating peer to peer (P2P) file sharing applications is by their degree of centralization, or how reliant the application is on a single central element.
-Some applications, like Napster, rely completely on a central server for organizing users and searching for files.
-This kind of structure simplifies system organization and ensures constant time searching.
-However, it places the burden of the entire system on the server.
-Therefore, server failure leads to a total loss of functionality.
-Other applications, like gnutella, have no central node, instead connecting users together and passing search requests between users.
-This removes the chance of system failure from loss of a single entity, but complicates the network and makes searching less efficient.
-The design decisions apparent in these applications affect virtually every aspect of their functionality and stability.
-\end{comment}
-
 Peer to peer (P2P) file sharing applications are some of the most well known and ubiquitous distributed systems in existance.
@@
 
- The novelty of PBJ lies within its connectivity. something something devised highly connected ultranode graph somethnig something redundancy something hops
+ The novelty of PBJ lies within its network structure.
+PBJ utilizes a central gateway to create and control highly connected network of users that emphasizes redundancy.
+By controlling how users are connected and maintaining network structure, PBJ decreases the number of hops needed to traverse the network.
 
@@
 Unlike Napster, which kept information about files on company machines, gnutella does not keep track of the files transferred on their system.
-This means that they are not liable if copyright infringement occurs on their system.
+This means that they are not liable if copyright infringment occurs on their system.
 
@@
 \end{figure}
-For PBJ, a novel algorithm for building the network was conceived that attempts to keep all of the nodes in a network within a few hops of each other.
+For PBJ, an algorithm for building the network was conceived that attempts to keep all of the nodes in a network within a few hops of each other.
 The basic algorithm for connecting ultra nodes in the network can be visualized as an outward spiral of ultra peers, as shown in Figure 1.
@@
 So for example, node 16 would connect with node 15 $(16 - 15 = 1 = 2^0)$, node 12 $(16 - 12 = 4 = 2^2)$, and node 0 $(16 - 0 = 16 = 2^4)$.
-
 A clear benefit of this structure is that the PBJ network has a high level of redundancy in the connections.
@@
 In this scheme of building the network, each ultra node`s sub network is filled before the next ultra node is created.
-This algorithm ensures that the graph has the smallest number of ultra nodes possible in a system and all but potentially the last ultra node have filled sub networks.
+This algorithm ensures that the graph has the smallest number of ultra nodes possible in a system since all existing ultra node sub networks must be filled before a new ultra node is created.
 
@@
 
-The PBJ client allows a shared path to be passed as a command line argument.
-The default share directory is a sub-directory named `share`.
+The PBJ client allows the user to share the contents of a directory.
+The default share directory is a sub-directory named `Share`.
 All files and sub directories in the user`s share directory will be available to the network for other nodes to download.
-When a user wants to search, they enter a keyword and submit a search request.
+As figure 2 shows, when a user wants to search for a file, they enter a keyword and submit a search request.
 The search request will be sent to the searching node`s ultra node (unless the node is itself an ultra node).
@@
 
- The ultra node will send the search request to all of the other peers in its sub network before broadcasting it to its connected ultra peers.
+ The ultra node will send the search request to all of the other peers in its sub network while simultaneously broadcasting it to its connected ultra peers.
 Search requests consist of four major parts - the searching node`s address, the keyword, a search id, and the time to live (ttl).
@@
 Various solutions were proposed, including updating the gateway, electing a node from the sub network to be a new ultra node, and the Ostrich approach (ignoring it).
-We eventually decided to implement a system of having the gateway check on existing ultra nodes.
+We eventually decided to implement a heartbeat system, where the gateway checks on existing ultra nodes.
 Upon receiving a request to add a new node to the network, the gateway pings every ultra node in the network.
@@
 The point here is to ensure that important connections in the network are rebuilt before attempting to refill the sub networks of ultra nodes.
-In addition, ultra nodes will occasionally ping their ultra peers and sub network.
+In addition, ultra nodes have a ÒheartbeatÓ; they occasionally ping their ultra peers and sub network.
 If an ultra node does not get a response from an ultra peer, it removes it from the list of connected ultra peers.
@@
 The instance of the Flask server is told to use a random port that is not currently in use.
-To install and use Flask a machine without modifying any system files, PBJ uses virtualenv ~\cite{virtual}, which is a tool used to create virtual Python environments.
+To install and use Flask on a machine without modifying any system files, PBJ uses virtualenv ~\cite{virtual}, which is a tool used to create virtual Python environments.
 A virtual Python environment can be created in a users home folder on a system using virtualenv, and then that user has permission to modify that environment however they wish.
 In this way, we were able to deploy a Python environment with the Flask module and its dependencies installed on every machine running PBJ.
-
 A concern when laying out the specification of how nodes would communicate was the case in which a node would have to communicate across a firewall.
@@
 \subsection{Test Plan}
-In order to test that PBJ is a stable and scalable system, we needed to design a solid testing plan.
 In the design phase of our project, we thoroughly discussed the use of Condor ~\cite{condor}, a HTC application that can deploy processes to a large number of computers, to test our network stability and search algorithms for large numbers of nodes.
 Unfortunately, the computers on Clemson`s Condor network are equipped with Windows Firewall, which blocks the access of ports that have not been explicitly granted permission.
-Instead, performed our testing on Clemson`s Palmetto cluster, a 12,000 core Linux cluster ~\cite{palmetto}.
+Instead, we ran tests on Clemson`s Palmetto cluster, a 12,000 core Linux cluster ~\cite{palmetto}.
 Our account on the cluster utilized a shared network drive between nodes, so we had to write a script that would create a unique share file in a unique share directory for every single node.
@@
 
+\begin{figure}[tbh]
+\centering
+\includegraphics[width=0.5\textwidth]{searchTime}
+\caption{Search Time to Reach All Nodes in a Network}
+\end{figure}
+
 \subsection{Analysis}
@@
 These numbers represent an idle network where the only messages being passed are search requests from ultra node 0.
-\begin{figure}[tbh]
-\centering
-\includegraphics[width=0.5\textwidth]{searchTime}
-\caption{Search Time to Reach All Nodes in a Network}
-\end{figure}
-
 In actual use, there would be many messages concurrently, so it is likely that search times would be higher than shown here.
@@
 
-\section{Future Work and Conclusion}
+\section{Conclusions and Future Work}
+
+PBJ is a decentralized file sharing system network building and search algorithms and node loss handling form the basis for a stable and reliable P2P application.
+PBJ users connect to the system through a dedicated gateway, either becoming ultra nodes connected to other ultra nodes or part of an ultra node`s sub network.
+To ensure the refilling of holes in the network, the gateway and the nodes have a ÒheartbeatÓ.
+The gateway maintains the structure of the network and will fill in missing ultra nodes to facilitate reliability and efficiency.
+Searching the network is done by keyword comparison to filenames, and search requests are broadcast between ultra peers.
+Results are reported to the searching node, which then has the option of downloading the file from any of the responding nodes.
+
+We tested the scalability of our network using Clemson Unversity`s Palmetto cluster, which allowed us to fill our network with 300 ultra nodes.
+To test the scalability of our network, we ran an automated test that measured the speed and distance traveled by a search request as the network grew in size.
+What we found is that even with 300 ultra nodes, the maximum number of hops that a search request took was only 8.
+Because there is no limit to the number of nodes in an ultra node`s sub network, this shows our network is able propagate a request to an extremely large number of nodes with a minimal number of hops.
 
@@
 Another concern we have is attempting to mitigate is leeching, the practice where by users of a file sharing network do not share any files to be downloaded but still use the network to get files.
-
-PBJ is a decentralized file sharing system whose highly connected nodes, search algorithm, and intelligent node loss handling form the ground work for a stable and reliable P2P application.
-PBJ is heavily influenced by existing file sharing services such as gnutella and to a much lesser extent Napster.
-
-PBJ users connect to the system through a dedicated gateway, either becoming ultra nodes connected to other ultra nodes or part of an ultra node`s sub network.
-Searching the network is done by keyword comparison to filenames, and search requests are broadcast between ultra peers.
-Results are reported to the searching node, which then has the option of downloading the file from any of the responding nodes.
-
-To ensure the refilling of holes in the network, the gateway and the nodes themselves periodically ping their connections.
-If an ultra peer does not respond to a ping, it is removed from the ultra node`s active connections.
-If a sub network node`s ultra node does not respond, the node will exit the network and attempt to reconnect through the gateway.
-Every time the gateway attempts add a node, it first checks that all of the existing ultra nodes are online.
-If one has lost connectivity, the new node to be added is added in that ultra node`s place.
-
-We tested the scalability of our network using Clemson Unversity`s Palmetto cluster, which allowed us to fill our network with 300 ultra nodes.
-To test the scalability of our network, we ran an automated test that measured the speed and distance traveled by a search request as the network grew in size.
-What we found is that even with 300 ultra nodes, the maximum number of hops that a search request took was 8.
-Because there is no limit to the number of nodes in an ultra node`s sub network, our network can propagate a request to an extremely large number of nodes with a minimal number of hops.
 

### 2012-01-18 paper/paper.tex
paper

@@
 One improvement which has been discussed is decentralizing the bootstrapping process by decentralizing the gateway.
-As our results show, the networkÕs performance improves once the total number of ultra nodes reaches an even power of 2.
+As our results show, the network`s performance improves once the total number of ultra nodes reaches an even power of 2.
 An algorithm that takes advantage of this trait would slightly alter how the network is built by the gateway.
@@
 This would help stabilize the network and improve quality.
-Improvements could also be made to PBJÕs search algorithm, specifically its handling of search ttl.
+Improvements could also be made to PBJ`s search algorithm, specifically its handling of search ttl.
 It may make sense to have a ttl that scales with the size of the network, or to remove ttl altogether from searching.

### 2012-01-18 paper/paper.tex
paper

@@
 The point here is to ensure that important connections in the network are rebuilt before attempting to refill the sub networks of ultra nodes.
-In addition, ultra nodes have a ÒheartbeatÓ; they occasionally ping their ultra peers and sub network.
+In addition, ultra nodes occasionally ping their ultra peers and sub network.
 If an ultra node does not get a response from an ultra peer, it removes it from the list of connected ultra peers.
@@
 
-Figure 3 shows the search time results show a positive linear trend with some obvious noise distortion.
+Figure 3 shows the search time results, which have a positive linear trend with some obvious noise distortion.
 Many of the spikes in search time are likely due to network latency.
@@
 We also feel that an explicit ttl will eventually limit PBJ`s scalability.
-Based on this testing, we have a number of future improvements to PBJ.
-These improvements would increase the network`s stability, decrease redundant traffic, and reach a larger percentage of the network.
 
@@
 PBJ users connect to the system through a dedicated gateway, either becoming ultra nodes connected to other ultra nodes or part of an ultra node`s sub network.
-To ensure the refilling of holes in the network, the gateway and the nodes have a ÒheartbeatÓ.
+To ensure the refilling of holes in the network, the gateway and the nodes have a ``heartbeat''.
 The gateway maintains the structure of the network and will fill in missing ultra nodes to facilitate reliability and efficiency.
@@
 Because there is no limit to the number of nodes in an ultra node`s sub network, this shows our network is able propagate a request to an extremely large number of nodes with a minimal number of hops.
+Based on this testing, we have a number of future improvements to PBJ.
+These improvements would increase the network`s stability, decrease redundant traffic, and reach a larger percentage of the network.
 
-In the future, we would like to pursue several possible improvements to PBJ.
 One improvement which has been discussed is decentralizing the bootstrapping process by decentralizing the gateway.
